
rm -r /QRISdata/Q2120/CELLECT_baseline2.1/*/*/CELLECT-LDSC/precomputation
rm -r /QRISdata/Q2120/CELLECT_baseline2.1/*/*/CELLECT-LDSC/logs
rm -r /QRISdata/Q2120/CELLECT_baseline2.1/*/*/CELLECT-LDSC/out/annots
rm /QRISdata/Q2120/CELLECT_baseline2.1/*/*/CELLECT-LDSC/out/prioritization/*.txt


rm -r /QRISdata/Q2120/CELLECT_baseline1.1/*/*/CELLECT-LDSC/precomputation
rm -r /QRISdata/Q2120/CELLECT_baseline1.1/*/*/CELLECT-LDSC/logs
rm -r /QRISdata/Q2120/CELLECT_baseline1.1/*/*/CELLECT-LDSC/out/annots
rm /QRISdata/Q2120/CELLECT_baseline1.1/*/*/CELLECT-LDSC/out/prioritization/*.txt


# Prepare the metrics
# Be careful of TDEP specificity being NA in genes, using 0 instead of NA

# Extract target CT based CELLECT input:
# TS
```{r}

library(data.table)
library(dplyr)

# Define the list of metrics
metrics <- c("cepo_norm", "det.esw_s", "esmu", "ges.esw_s", "nsi.esw_s", "sclinker", "ep.esw_s", "TDEP")

# Define file paths
input_dir <- "/scratch/project/genetic_data_analysis/uqali4/benchmark/cellex_out/"
output_dir <- "/scratch/project/genetic_data_analysis/uqali4/cellex_out/"
aim_ct_file <- "/home/uqali4/ts_CT_Sep19.txt"

# Read aim_ct (target columns)
aim_ct <- fread(aim_ct_file, header = FALSE)$V1

# Loop through each metric and apply the logic
for (metric in metrics) {
  # Construct input and output file paths
  input_file <- paste0(input_dir, "ts_pc.", metric, ".csv.gz")
  output_file <- paste0(output_dir, "ts_conLDSC_target_Sep19_pc.", metric, ".csv")
  
  # Read the input file
  combined_dt <- fread(input_file)
  names(combined_dt)[1]="gene"
  
  # Select "gene" and columns in aim_ct
  dt_save <- combined_dt %>% select("gene", all_of(aim_ct))
  # Find rows where any column has NA
  #rows_with_na <- dt_save[apply(is.na(dt_save), 1, any), ]
  # Display the rows with NA
  #dim(rows_with_na)
  dt_save[is.na(dt_save)] <- 0
  # Write the output file
  write.table(dt_save, file = output_file, row.names = FALSE, col.names = TRUE, quote = FALSE, sep = ",")
  
  # Print a message indicating completion
  cat("Processed:", dim(combined_dt), "\n")
  cat("Processed:", metric, "\n")
}


```

# TMS
```{r}

library(data.table)
library(dplyr)

# Define the list of metrics
metrics <- c("cepo_norm", "det.esw_s", "esmu", "ges.esw_s", "nsi.esw_s", "sclinker", "ep.esw_s", "TDEP")

# Define file paths
input_dir <- "/scratch/project/genetic_data_analysis/uqali4/benchmark/cellex_out/"
output_dir <- "/scratch/project/genetic_data_analysis/uqali4/cellex_out/"
aim_ct_file <- "/home/uqali4/tms_CT_Sep19.txt"

# Read aim_ct (target columns)
aim_ct <- fread(aim_ct_file, header = FALSE)$V1

# Loop through each metric and apply the logic
for (metric in metrics) {
  # Construct input and output file paths
  input_file <- paste0(input_dir, "tms_pc.", metric, ".csv.gz")
  output_file <- paste0(output_dir, "tms_conLDSC_target_Sep19_pc.", metric, ".csv")
  
  # Read the input file
  combined_dt <- fread(input_file)
  names(combined_dt)[1]="gene"
  
  # Select "gene" and columns in aim_ct
  dt_save <- combined_dt %>% select("gene", all_of(aim_ct))
  
  # Write the output file
  write.table(dt_save, file = output_file, row.names = FALSE, col.names = TRUE, quote = FALSE, sep = ",")
  
  # Print a message indicating completion
  cat("Processed:", dim(combined_dt), "\n")
  cat("Processed:", metric, "\n")
}


```

# Make a template in ~/Manuscript_Ang/Benchmark_comparison/Code/Code_final/tms_cepo_norm_v1.1.yml
mkdir -p /QRISdata/Q5514/CELLECT_baseline1.1/op_Sep19_tms_pc/cepo_norm


# Do a test:
```{bash}
conda activate cellct_2
mamba activate snakemake
dir="/scratch/project/genetic_data_analysis/uqali4/new_conda_env/CELLECT"
config_dir="/home/uqali4/Sep19_scripts"
cd /scratch/project/genetic_data_analysis/uqali4/CELLECT
snakemake --use-conda -j 20 -s ${dir}/cellect-ldsc.snakefile --configfile ${config_dir}/tms_Sep19_cepo_norm_v1.1.yml

conda activate cellct_2
mamba activate snakemake
dir="/scratch/project/genetic_data_analysis/uqali4/new_conda_env/CELLECT"
config_dir="/home/uqali4/Sep19_scripts/v2.1"
cd /scratch/project/genetic_data_analysis/uqali4/CELLECT
snakemake --use-conda -j 20 -s ${dir}/cellect-ldsc.snakefile --configfile ${config_dir}/TDEP_ts_v2.1.yml


conda activate cellct_2
mamba activate snakemake
dir="/scratch/project/genetic_data_analysis/uqali4/new_conda_env/CELLECT"
config_dir="/home/uqali4/Sep19_scripts/v1.1"
cd /scratch/project/genetic_data_analysis/uqali4/CELLECT
snakemake --use-conda -j 20 -s ${dir}/cellect-ldsc.snakefile --configfile ${config_dir}/TDEP_ts_v1.1.yml



```

# Revise the metrics file names:
```{bash}
#!/bin/bash

# Directory containing the files
directory="/scratch/project/genetic_data_analysis/uqali4/cellex_out/"

# List of metrics that need to be revised by replacing '.' with '_'
metrics=("det.esw_s" "ges.esw_s" "nsi.esw_s" "ep.esw_s")

# List of file prefixes
file_prefixes=(
  "tms_conLDSC_target_Sep19_pc"
  "ts_conLDSC_target_Sep19_pc"
)

# Loop through each prefix and metric to find and rename files
for prefix in "${file_prefixes[@]}"; do
  for metric in "${metrics[@]}"; do
    # Construct the old filename pattern
    old_filename="${directory}/${prefix}.${metric}.csv"

    # Construct the new filename by replacing '.' with '_' in the metric
    new_metric="${metric//./_}"
    new_filename="${directory}/${prefix}.${new_metric}.csv"

    # Check if the old file exists
    if [ -f "$old_filename" ]; then
      # Rename the file
      echo "Renaming $old_filename to $new_filename"
      mv "$old_filename" "$new_filename"
    else
      echo "File not found: $old_filename"
    fi
  done
done


```


# Shell Script to Create Directories
```{bash}

 #!/bin/bash

# Define the file prefixes and metrics
file_prefixes=("Sep19_tms_pc") 

metrics=("cepo_norm" "det_esw_s" "esmu" "ges_esw_s" "nsi_esw_s" "sclinker" "ep_esw_s" "TDEP")

# Base directory path
base_dir="/QRISdata/Q5514/CELLECT_baseline1.1"

# Loop through all combinations of prefixes and metrics
for prefix in "${file_prefixes[@]}"; do
  for metric in "${metrics[@]}"; do
    # Construct the full directory path
    dir_path="${base_dir}/op_${prefix}/${metric}"
    
    # Create the directory with mkdir -p
    mkdir -p "$dir_path"
    
    # Print a message indicating the directory creation
    echo "Created directory: $dir_path"
  done
done

####################################################################################################

####################################################################################################


file_prefixes=("Sep19_ts_pc")

metrics=("cepo_norm" "det_esw_s" "esmu" "ges_esw_s" "nsi_esw_s" "sclinker" "ep_esw_s" "TDEP")

# Base directory path
base_dir="/QRISdata/Q2120/CELLECT_baseline1.1"

# Loop through all combinations of prefixes and metrics
for prefix in "${file_prefixes[@]}"; do
  for metric in "${metrics[@]}"; do
    # Construct the full directory path
    dir_path="${base_dir}/op_${prefix}/${metric}"
    
    # Create the directory with mkdir -p
    mkdir -p "$dir_path"
    
    # Print a message indicating the directory creation
    echo "Created directory: $dir_path"
  done
done



```


# Shell Script to Create Directories
```{bash}

file_prefixes=("Sep19_tms_pc") 

metrics=("cepo_norm" "det_esw_s" "esmu" "ges_esw_s" "nsi_esw_s" "sclinker" "ep_esw_s" "TDEP")

# Base directory path
base_dir="/QRISdata/Q5514/CELLECT_baseline2.1"

# Loop through all combinations of prefixes and metrics
for prefix in "${file_prefixes[@]}"; do
  for metric in "${metrics[@]}"; do
    # Construct the full directory path
    dir_path="${base_dir}/op_${prefix}/${metric}"
    
    # Create the directory with mkdir -p
    mkdir -p "$dir_path"
    
    # Print a message indicating the directory creation
    echo "Created directory: $dir_path"
  done
done


####################################################################################################

####################################################################################################


file_prefixes=("Sep19_ts_pc")

metrics=("cepo_norm" "det_esw_s" "esmu" "ges_esw_s" "nsi_esw_s" "sclinker" "ep_esw_s" "TDEP")

# Base directory path
base_dir="/QRISdata/Q2120/CELLECT_baseline2.1"

# Loop through all combinations of prefixes and metrics
for prefix in "${file_prefixes[@]}"; do
  for metric in "${metrics[@]}"; do
    # Construct the full directory path
    dir_path="${base_dir}/op_${prefix}/${metric}"
    
    # Create the directory with mkdir -p
    mkdir -p "$dir_path"
    
    # Print a message indicating the directory creation
    echo "Created directory: $dir_path"
  done
done



```


```{r}
setwd("/home/uqali4/Sep19_scripts/v1.1")

# Define the file prefixes and metrics
file_prefixes <- c("tms")
metrics <- c("cepo_norm", "det_esw_s", "esmu", "ges_esw_s", "nsi_esw_s", "sclinker", "ep_esw_s", "TDEP")

# Read the template file content
template_file <- "/home/uqali4/Sep19_scripts/tms_cepo_norm_v1.1.yml"
template_content <- readLines(template_file)

# Function to generate .yml files
generate_yml <- function(prefix, metric) {
    # Step-by-step replacement to ensure correct changes
    new_content <- template_content
    
    # Replace 'tms' with the correct prefix
    new_content <- gsub("tms", prefix, new_content)
    
    # Replace 'cepo_norm' with the correct metric
    new_content <- gsub("cepo_norm", metric, new_content)
    
    # Replace the specific file paths for the metric
    new_content <- gsub("/QRISdata/Q5514/CELLECT_baseline1.1/op_Sep19_tms_pc/cepo_norm",
                        paste0("/QRISdata/Q5514/CELLECT_baseline1.1/op_Sep19_", prefix, "_pc/", metric),
                        new_content)
    
    new_content <- gsub("/scratch/project/genetic_data_analysis/uqali4/cellex_out/tms_conLDSC_target_Sep19_pc.cepo_norm.csv",
                        paste0("/scratch/project/genetic_data_analysis/uqali4/cellex_out/", prefix, "_conLDSC_target_Sep19_pc.", metric, ".csv"),
                        new_content)
    
    # Define the output file name
    output_file <- paste0(metric, "_", prefix, "_v1.1.yml")
    
    # Write the new content to a new .yml file
    writeLines(new_content, con = output_file)
}

# Loop through all combinations of prefixes and metrics to generate .yml files
for (prefix in file_prefixes) {
    for (metric in metrics) {
        generate_yml(prefix, metric)
    }
}



##############################################################################
setwd("/home/uqali4/Sep19_scripts/v2.1")

# Define the file prefixes and metrics
file_prefixes <- c("tms")
metrics <- c("cepo_norm", "det_esw_s", "esmu", "ges_esw_s", "nsi_esw_s", "sclinker", "ep_esw_s", "TDEP")

# Read the template file content
template_file <- "/home/uqali4/Sep19_scripts/tms_cepo_norm_v1.1.yml"
template_content <- readLines(template_file)

# Function to generate .yml files
generate_yml <- function(prefix, metric) {
    # Step-by-step replacement to ensure correct changes
    new_content <- template_content
    
    # Replace 'tms' with the correct prefix
    new_content <- gsub("tms", prefix, new_content)
    
    # Replace 'cepo_norm' with the correct metric
    new_content <- gsub("cepo_norm", metric, new_content)
    
    # Replace '/QRISdata/Q5514/' with '/QRISdata/Q2120/' 
    # (this ensures the base path is correctly replaced first)
    new_content <- gsub("CELLECT_baseline1.1", "CELLECT_baseline2.1", new_content)
    
    # Replace the specific file paths for the metric
    new_content <- gsub("/QRISdata/Q5514/CELLECT_baseline2.1/op_Sep19_tms_pc/cepo_norm",
                        paste0("/QRISdata/Q5514/CELLECT_baseline2.1/op_Sep19_", prefix, "_pc/", metric),
                        new_content)
    
    new_content <- gsub("/scratch/project/genetic_data_analysis/uqali4/cellex_out/tms_conLDSC_target_Sep19_pc.cepo_norm.csv",
                        paste0("/scratch/project/genetic_data_analysis/uqali4/cellex_out/", prefix, "_conLDSC_target_Sep19_pc.", metric, ".csv"),
                        new_content)
    
    # Define the output file name
    output_file <- paste0(metric, "_", prefix, "_v2.1.yml")
    
    # Write the new content to a new .yml file
    writeLines(new_content, con = output_file)
}

# Loop through all combinations of prefixes and metrics to generate .yml files
for (prefix in file_prefixes) {
    for (metric in metrics) {
        generate_yml(prefix, metric)
    }
}


```



```{r}
setwd("/home/uqali4/Sep19_scripts/v1.1")

# Define the file prefixes and metrics
file_prefixes <- c("ts")
metrics <- c("cepo_norm", "det_esw_s", "esmu", "ges_esw_s", "nsi_esw_s", "sclinker", "ep_esw_s", "TDEP")

# Read the template file content
template_file <- "/home/uqali4/Sep19_scripts/tms_cepo_norm_v1.1.yml"
template_content <- readLines(template_file)

# Function to generate .yml files
generate_yml <- function(prefix, metric) {
    # Step-by-step replacement to ensure correct changes
    new_content <- template_content
    
    # Replace 'tms' with the correct prefix
    new_content <- gsub("tms", prefix, new_content)
    
    # Replace 'cepo_norm' with the correct metric
    new_content <- gsub("cepo_norm", metric, new_content)
    
    # Replace '/QRISdata/Q5514/' with '/QRISdata/Q2120/' 
    # (this ensures the base path is correctly replaced first)
    new_content <- gsub("/QRISdata/Q5514/", "/QRISdata/Q2120/", new_content)
    
    # Replace the specific file paths for the metric
    new_content <- gsub("/QRISdata/Q2120/CELLECT_baseline1.1/op_Sep19_tms_pc/cepo_norm",
                        paste0("/QRISdata/Q2120/CELLECT_baseline1.1/op_Sep19_", prefix, "_pc/", metric),
                        new_content)
    
    new_content <- gsub("/scratch/project/genetic_data_analysis/uqali4/cellex_out/tms_conLDSC_target_Sep19_pc.cepo_norm.csv",
                        paste0("/scratch/project/genetic_data_analysis/uqali4/cellex_out/", prefix, "_conLDSC_target_Sep19_pc.", metric, ".csv"),
                        new_content)
    
    # Define the output file name
    output_file <- paste0(metric, "_", prefix, "_v1.1.yml")
    
    # Write the new content to a new .yml file
    writeLines(new_content, con = output_file)
}

# Loop through all combinations of prefixes and metrics to generate .yml files
for (prefix in file_prefixes) {
    for (metric in metrics) {
        generate_yml(prefix, metric)
    }
}



##############################################################################
setwd("/home/uqali4/Sep19_scripts/v2.1")

# Define the file prefixes and metrics
file_prefixes <- c("ts")
metrics <- c("cepo_norm", "det_esw_s", "esmu", "ges_esw_s", "nsi_esw_s", "sclinker", "ep_esw_s", "TDEP")

# Read the template file content
template_file <- "/home/uqali4/Sep19_scripts/tms_cepo_norm_v1.1.yml"
template_content <- readLines(template_file)

# Function to generate .yml files
generate_yml <- function(prefix, metric) {
    # Step-by-step replacement to ensure correct changes
    new_content <- template_content
    
    # Replace 'tms' with the correct prefix
    new_content <- gsub("tms", prefix, new_content)
    
    # Replace 'cepo_norm' with the correct metric
    new_content <- gsub("cepo_norm", metric, new_content)
    
    # Replace '/QRISdata/Q5514/' with '/QRISdata/Q2120/' 
    # (this ensures the base path is correctly replaced first)
    new_content <- gsub("/QRISdata/Q5514/", "/QRISdata/Q2120/", new_content)
    new_content <- gsub("CELLECT_baseline1.1", "CELLECT_baseline2.1", new_content)
    
    # Replace the specific file paths for the metric
    new_content <- gsub("/QRISdata/Q2120/CELLECT_baseline2.1/op_Sep19_tms_pc/cepo_norm",
                        paste0("/QRISdata/Q2120/CELLECT_baseline2.1/op_Sep19_", prefix, "_pc/", metric),
                        new_content)
    
    new_content <- gsub("/scratch/project/genetic_data_analysis/uqali4/cellex_out/tms_conLDSC_target_Sep19_pc.cepo_norm.csv",
                        paste0("/scratch/project/genetic_data_analysis/uqali4/cellex_out/", prefix, "_conLDSC_target_Sep19_pc.", metric, ".csv"),
                        new_content)
    
    # Define the output file name
    output_file <- paste0(metric, "_", prefix, "_v2.1.yml")
    
    # Write the new content to a new .yml file
    writeLines(new_content, con = output_file)
}

# Loop through all combinations of prefixes and metrics to generate .yml files
for (prefix in file_prefixes) {
    for (metric in metrics) {
        generate_yml(prefix, metric)
    }
}


```



ls /scratch/project/genetic_data_analysis/uqali4/cellex_out/*_conLDSC_target_Sep19_pc.*.csv



# Submit all combinations

```{bash}
#!/bin/bash
conda activate cellct_2
mamba activate snakemake

# Directories and paths
dir="/scratch/project/genetic_data_analysis/uqali4/new_conda_env/CELLECT"
config_dir_v1="/home/uqali4/Sep19_scripts/v1.1"
config_dir_v2="/home/uqali4/Sep19_scripts/v2.1"
snakefile_v1="cellect-ldsc.snakefile"
snakefile_v2="cellect-ldsc_AL.snakefile"
workdir="/scratch/project/genetic_data_analysis/uqali4/CELLECT"

# List of metrics
metrics=("cepo_norm" "TDEP" "sclinker" "esmu" "det_esw_s" "ges_esw_s" "nsi_esw_s" "ep_esw_s")

# Function to submit Snakemake jobs for a given version, prefix, and metrics
submit_jobs_for_prefix() {
  local config_dir="$1"
  local snakefile="$2"
  local prefix="$3"
  local version="$4"  # Add a parameter for version

  # Loop over all metrics for the given prefix
  for metric in "${metrics[@]}"; do
    # Construct the correct pattern to find .yml files containing the prefix and metric
    config_file="${config_dir}/${metric}_${prefix}_${version}.yml"
    
    # Check if the config file exists
    if [ -f "$config_file" ]; then
      # Extract the base name of the config file for output readability
      base_name=$(basename "$config_file")
      
      # Print the current job being submitted
      echo "Submitting job for config file: $base_name"
      
      # Submit the Snakemake job
      snakemake --use-conda -j 20 -s "${dir}/${snakefile}" --configfile "${config_file}"
    else
      echo "No config file found for: ${metric}_${prefix}_${version}.yml"
    fi
  done
}

# Activate the environment and change to working directory
cd $workdir

# Submit jobs for each prefix separately with correct version


# Submit jobs for version 1.1
submit_jobs_for_prefix "$config_dir_v1" "$snakefile_v1" "tms" "v1.1"

# Submit jobs for version 2.1
submit_jobs_for_prefix "$config_dir_v2" "$snakefile_v2" "tms" "v2.1" 

# Submit jobs for version 1.1
submit_jobs_for_prefix "$config_dir_v1" "$snakefile_v1" "ts" "v1.1"

# Submit jobs for version 2.1
submit_jobs_for_prefix "$config_dir_v2" "$snakefile_v2" "ts" "v2.1"



```


# save and merge 
```{r}

library(dplyr)
library(readr)
library(tidyr)

# Define the metrics
metrics <- c("cepo_norm", "det_esw_s", "esmu", "ges_esw_s", "nsi_esw_s", "sclinker", "ep_esw_s", "TDEP")

# Define the base paths
base_paths <- list(
  baseline1.1_tms = "/QRISdata/Q5514/CELLECT_baseline1.1/op_Sep19_tms_pc/",
  baseline1.1_ts = "/QRISdata/Q2120/CELLECT_baseline1.1/op_Sep19_ts_pc/",
  baseline2.1_tms = "/QRISdata/Q5514/CELLECT_baseline2.1/op_Sep19_tms_pc/",
  baseline2.1_ts = "/QRISdata/Q2120/CELLECT_baseline2.1/op_Sep19_ts_pc/"
)


# Function to read and annotate a CSV file
read_and_annotate <- function(file_path, dataset, metric, baseline) {
  read_csv(file_path) %>%
    mutate(Dataset = dataset, Metrics = metric, Baseline = baseline)
}

# Initialize an empty list to store data frames
data_list <- list()

# Loop through each base path and metric to read and annotate the data
for (base_name in names(base_paths)) {
  base_path <- base_paths[[base_name]]
  # Extract dataset and baseline from the base_name
  dataset <- ifelse(grepl("tms", base_name), "tms", "ts")
  baseline <- ifelse(grepl("baseline1.1", base_name), "v1.1", "v2.1")
  for (metric in metrics) {
    file_path <- file.path(base_path, metric, "CELLECT-LDSC/results/prioritization.csv")
    if (file.exists(file_path)) {
      data_list[[length(data_list) + 1]] <- read_and_annotate(file_path, dataset, metric, baseline)
    }
  }
}

# Combine all data frames into one
merged_data <- bind_rows(data_list)


# Save the merged data to a new file
write_csv(merged_data, "/scratch/user/uqali4/tms_ts_conLDSC_Sep19.csv")

```


scp -r uqali4@bunya.rcc.uq.edu.au:"/scratch/user/uqali4/tms_ts_conLDSC_Sep19.csv" /Users/uqali4/Manuscripts/Benchmark/Results/









