

scp -r /Users/uqali4/Manuscripts/Benchmark/CT_fig_ditinct_datasets.txt  uqali4@bunya.rcc.uq.edu.au:/scratch/user/uqali4/
scp -r uqali4@bunya.rcc.uq.edu.au:/scratch/project/genetic_data_analysis/uqali4/MG_set_conAnnot/sclinker_s_Cepo_s_differences_in_headers.csv ~/Manuscripts/Benchmark/Results/


# Check the differece in Cepo_s and sclinker_s based results since Cepo removed a lot of cell type because of Cepo forced:
```{r}
library(data.table)
# Define the directory containing the CSV files
input_dir <- "/scratch/project/genetic_data_analysis/uqali4/MG_set_conAnnot/"

# Get a list of all the csv files in the directory
file_list <- list.files(input_dir, pattern = ".csv$", full.names = TRUE)

# Split the files into Cepo and sclinker files
cepo_files <- file_list[grepl("Cepo_s.csv$", file_list)]
sclinker_files <- file_list[grepl("sclinker_s.csv$", file_list)]

# Initialize an empty data table to store results
diff_columns_dt <- data.table(dataset = character(), cell_type = character(), metric = character())

# Loop through each Cepo file and find its corresponding sclinker file
for (i in seq_along(cepo_files)) {
  cepo_file <- cepo_files[i]
  sclinker_file <- sclinker_files[i]

  # Extract dataset prefix from filename
  dataset_prefix <- gsub(".Cepo_s.csv", "", basename(cepo_file))
  
  # Read only the header to get column names for both files
  cepo <- fread(cepo_file)
  cepo_header <- names(cepo)
  sclinker <- fread(sclinker_file)
  sclinker_header <- names(sclinker)
  
  # Find differences between the headers
  cepo_only <- setdiff(cepo_header, sclinker_header)
  sclinker_only <- setdiff(sclinker_header, cepo_header)
  
  # Collect the differences in a data table
  if (length(cepo_only) > 0) {
    diff_columns_dt <- rbind(diff_columns_dt, data.table(dataset = dataset_prefix, cell_type = cepo_only, metric = "Cepo only"))
  }
  if (length(sclinker_only) > 0) {
    diff_columns_dt <- rbind(diff_columns_dt, data.table(dataset = dataset_prefix, cell_type = sclinker_only, metric = "sclinker only"))
  }
}

# Save the resulting data table to a CSV file
output_file <- file.path(input_dir, "sclinker_s_Cepo_s_differences_in_headers.csv")
fwrite(diff_columns_dt, output_file, row.names = FALSE)



```


# Read in Marker genes for cell types.
```{r}
library(data.table)
library(dplyr)
library(readr)
library(stringr)
library(tidyr)

# Load the cell types mapping file
cell_types_df <- fread("/scratch/user/uqali4/CT_fig_ditinct_datasets.txt") %>%
  filter(!(Dataset == "TS" & CT_fig == "ventricular myocyte"))

# Function to extract dataset name, metrics, and gene_group from file name
extract_info_from_filename <- function(filename) {
  # Remove the full path
  base_name <- basename(filename)
  
  # Extract gene group
  gene_group <- ifelse(grepl("_pc", base_name), "PCgenes", "allgene")
  
  # Extract metrics and dataset name
  parts_orig <- str_split(base_name, "\\.")[[1]]
  
  base_name_simp <- gsub("_pc", "", base_name)
  parts <- str_split(base_name_simp, "\\.")[[1]]
  
  dataset <- parts_orig[1]
  metrics <- parts[2]

  return(list(dataset = dataset, metrics = metrics, gene_group = gene_group))
}


# Function to filter cell types and retain only relevant columns
process_file <- function(file_path, cell_types_df) {
    # Read the file
    data <- fread(file_path)
    names(data)[1] <- "ENSG"  # Rename the first column to "ENSG" (gene name)

    # Extract dataset, metrics, and gene_group info from file name
    file_info <- extract_info_from_filename(file_path)

    # Filter the cell types that are needed for the current dataset
    relevant_cell_types_df <- cell_types_df %>%
      filter(Dataset_02 == file_info$dataset)  # Filter relevant dataset

    # Extract CT_ldsc and corresponding CT_fig
    relevant_cell_types <- relevant_cell_types_df$CT_ldsc

    # Keep only relevant columns (gene name and relevant cell types)
    relevant_cols <- c("ENSG", relevant_cell_types)
    filtered_data <- data %>%
      select(any_of(relevant_cols))  # Keep only relevant columns

    # Rename the cell type columns from CT_ldsc to CT_fig
    ct_fig_names <- relevant_cell_types_df$CT_fig
    
    colnames(filtered_data)[-1] <- ct_fig_names  # Rename cell type columns

    # Add dataset, metrics, and gene_group columns to the filtered data
    filtered_data <- filtered_data %>%
      mutate(Dataset = file_info$dataset,
             Metrics = file_info$metrics,
             Gene_Group = file_info$gene_group)

    return(filtered_data)
}
    
# Directory with the input files
#input_dir <- "/QRISdata/Q2120/group_move/MG_set_conAnnot/"
input_dir <- "/scratch/project/genetic_data_analysis/uqali4/MG_set_conAnnot/"

# Get a list of all the csv files in the directory
file_list <- list.files(input_dir, pattern = "\\_s.csv$", full.names = TRUE) # 36 files in total
file_list_tmp=file_list[1:36]

# Initialize all_data
all_data <- NULL

# Process each file and combine the results
all_data <- lapply(file_list_tmp, process_file, cell_types_df = cell_types_df) %>% bind_rows()

all_data$Dataset <- gsub("_pc", "", all_data$Dataset)

library(dplyr)

# Adjust dataset name for known mappings
all_data <- all_data %>%
  mutate(Dataset = case_when(
    Dataset == "CARE_snRNA_Heart" ~ "CARE",
    Dataset == "CARE_snRNA_Heart_expr_gene_withPos" ~ "CARE",
    Dataset == "Cheng_2018_Cell_Reports" ~ "Cheng_2018_Cell_Reports_updated",
    Dataset == "HLCA_core_healthy_LP_expr_gene_withPos" ~ "HLCA_core_healthy_LP",
    Dataset == "Kamath_2022_normal_expr_gene_withPos" ~ "Kamath_2022_normal",
    Dataset == "tms_facs_1to1" ~ "TMS",
    Dataset == "ts_1to1" ~ "TS",
    TRUE ~ Dataset
  ))

write_csv(all_data, "/scratch/user/uqali4/combined_target_cell_types_sclinker_s_cepo_s.csv")



# Loop through each file and print the header names
for (file in file_list) {
  # Read only the header (first row) to get column names
  header <- read.csv(file, nrows = 1, check.names = FALSE)
  
  # Print the file name and its header names
  cat("File:", file, "\n")
  cat("Header names:", paste(colnames(header), collapse = ", "), "\n\n")
}


CT_marker=fread("/scratch/user/uqali4/CT_fig_ditinct_with_marker_genes_complete.txt")

# Convert the 'CT_marker' data to the format of one gene in one row
formatted_CT_marker <- CT_marker %>%
  # Separate the marker_genes by commas into individual gene names
  separate_rows(marker_genes, sep = ", ") %>%
  # Rename columns for consistency with desired output
  rename(gene_name = marker_genes, cell_type = CT_fig) %>%
  # Optionally, you can trim any extra spaces from gene_name or cell_type
  mutate(gene_name = trimws(gene_name),
         cell_type = trimws(cell_type)) %>%
  select(!reference)




# Convert the data to long format
long_format <- melt(all_data, 
                    id.vars = c("ENSG", "Dataset", "Metrics", "Gene_Group"),  # Columns to keep in the long format
                    variable.name = "cell_type",  # Name for the cell type column
                    value.name = "specificity")  # Name for the values in the long format

head(long_format)

# Match the ensgid genes in the data to symbol genes
gene_mat <- fread("/QRISdata/Q5059/mBAT/mBAT-main/geneMatrix.tsv") %>% select(ensgid, gene_name, gene_type)
gene_dt <- inner_join(long_format %>% dplyr::rename(ensgid = ENSG), gene_mat)


organ_mapping <- c("Cheng_2018_Cell_Reports_updated" = "Skin",
                   "Fasolino_2022_Nat_Metab_normal_only" = "Pancreas",
                   "2019_Smillie_normal_cellxgene" = "Colon",
                   "human_liver_atlas_Guilliams_2022_cell" = "Liver",
                   "FBM_Jardine_2021_Nature" = "Bone Marrow and blood",
                   "Kamath_2022_normal" = "Brain",
                   "CARE" = "Heart",
                   "HLCA_core_healthy_LP" = "Lung",
                   "TMS" = "Atlas - Mouse",
                   "TS" = "Atlas - Human")

# Assign the organ values based on the study column
gene_dt$organ <- organ_mapping[gene_dt$Dataset]

setDT(gene_dt) 
gene_dt[, rank := frank(-specificity, ties.method = "average"), by = .(Metrics, Dataset, Gene_Group, cell_type)]
write_csv(gene_dt, "/scratch/user/uqali4/combined_target_cell_types_sclinker_s_cepo_s.csv") #Now save: /QRISdata/Q2120/CT_specificity/




# Extract top 1000 genes based on specificity within each unique combination of Metrics, Dataset, and cell_type
top_1000_genes <- gene_dt %>%
  group_by(Metrics, Dataset, cell_type) %>%
  slice_max(order_by = specificity, n = 1000, with_ties = FALSE) %>%
  ungroup()


# Recalculate rank within each unique combination of Metrics, Dataset, and cell_type
setDT(top_1000_genes)
top_1000_genes[, rank := frank(-specificity, ties.method = "average"), by = .(Metrics, Dataset, Gene_Group, cell_type)]
head(top_1000_genes)


write_csv(top_1000_genes, "/scratch/user/uqali4/combined_target_cell_types_sclinker_s_cepo_s_rank_top1000.csv")

combined_data_CT_top_1000 <- top_1000_genes %>% 
  inner_join(formatted_CT_marker, by = c("gene_name", "cell_type")) %>%
  select(gene_name, cell_type, Metrics, rank, Gene_Group, organ) 

head(combined_data_CT_top_1000)
write.table(combined_data_CT_top_1000,"/scratch/user/uqali4/Fig3A_relevence_1k_sclinker_s_cepo_s.txt",row.names=F,col.names=T,quote=F,sep="\t")

```

scp -r uqali4@bunya.rcc.uq.edu.au:/scratch/user/uqali4/Fig3A_relevence_1k_sclinker_s_cepo_s.txt /Users/uqali4/Manuscripts/Benchmark/















































