By default, the testing direction is set to one-sided, positive for gene sets [Binary] and to two-sided for gene properties [Continuous].

# MGset-com from cepo_s and sclinker_s
# add_MG_atlas, add_MG_organ  [Not use]
```{r}
cepo_s_MG = fread("~/Manuscript_Ang/Benchmark_comparison/cepo_s_MAGMAgeneset_continuous_oneside_results.txt")

sclinker_s_MG = fread("~/Manuscript_Ang/Benchmark_comparison/sclinker_s_MAGMAgeneset_continuous_oneside_results.txt")
sclinker_s_MG$Dataset[sclinker_s_MG$Dataset == "CARE_pc_only"] <- "CARE_snRNA_Heart_pc"
sclinker_s_MG$Dataset[sclinker_s_MG$Dataset == "CARE_all_genes"] <- "CARE_snRNA_Heart_expr_gene_withPos"
sclinker_s_MG$Dataset[sclinker_s_MG$Dataset == "Kamath_pc_only"] <- "Kamath_2022_normal_pc"
sclinker_s_MG$Dataset[sclinker_s_MG$Dataset == "Kamath_allgenes"] <- "Kamath_2022_normal_expr_gene_withPos"
sclinker_s_MG$Dataset[sclinker_s_MG$Dataset == "HCLA_LP_allgenes"] <- "HLCA_core_healthy_LP_expr_gene_withPos"

# For cepo_s_MG
cepo_s_MG <- cepo_s_MG %>%
  mutate(
    gene_group = ifelse(grepl("_pc$", Dataset), "PCgene", "allgene"),
    Dataset = gsub("_expr_gene", "", Dataset),
    Dataset = gsub("_pc", "", Dataset),
    Dataset = gsub("_withPos", "", Dataset)
  )

cepo_s_MG$Dataset[cepo_s_MG$Dataset == "Cheng_2018_Cell_Reports"] <- "Cheng_2018_Cell_Reports_updated"
cepo_s_MG$Dataset[cepo_s_MG$Dataset == "CARE_snRNA_Heart"] <- "CARE"

cepo_s_MG_tmp <- inner_join(
  cepo_s_MG %>% dplyr::rename(file = Trait),
  Trait_dt %>% select(Phenotype, file)
) %>% select(!c("file"))

# For sclinker_s_MG
sclinker_s_MG <- sclinker_s_MG %>%
  mutate(
    gene_group = ifelse(grepl("_pc$", Dataset), "PCgene", "allgene"),
    Dataset = gsub("_expr_gene", "", Dataset),
    Dataset = gsub("_pc", "", Dataset),
    Dataset = gsub("_withPos", "", Dataset)
  )

sclinker_s_MG$Dataset[sclinker_s_MG$Dataset == "Cheng_2018_Cell_Reports"] <- "Cheng_2018_Cell_Reports_updated"
sclinker_s_MG$Dataset[sclinker_s_MG$Dataset == "CARE_snRNA_Heart"] <- "CARE"

sclinker_s_MG_tmp <- inner_join(
  sclinker_s_MG %>% dplyr::rename(file = Trait),
  Trait_dt %>% select(Phenotype, file)
) %>% select(!c("file"))


add_MG = rbind(sclinker_s_MG_tmp,cepo_s_MG_tmp)
add_MG$Dataset[add_MG$Dataset == "ts"] <- "Human"
add_MG$Dataset[add_MG$Dataset == "tms"] <- "Mouse"

add_MG <- add_MG %>%
  mutate(FULL_NAME = case_when(
   Dataset == "HLCA_core_healthy_LP" & FULL_NAME == "CD8_positive__alpha_beta_T_cell" ~ "CD8.positive__alpha.beta_T_cell",
   Dataset == "HLCA_core_healthy_LP" & FULL_NAME == "CD4_positive__alpha_beta_T_cell" ~ "CD4.positive__alpha.beta_T_cell",
    TRUE ~ FULL_NAME  # Keep all other values unchanged
  )) %>% dplyr::rename(CT_ldsc="FULL_NAME")

add_MG = inner_join(add_MG, Trait_dt2%>%select(Phenotype,CT_ldsc,CT_fig,Dataset,Property,`Chategory [Follow by Phenotype]`)) %>% mutate(CT_Pheno = paste(CT_fig, Phenotype, sep = "_"), Annotation="Continuous-one-side")


organ_mapping <- c("Cheng_2018_Cell_Reports_updated" = "Skin",
                   "Fasolino_2022_Nat_Metab_normal_only" = "Pancreas",
                   "2019_Smillie_normal_cellxgene" = "Colon",
                   "human_liver_atlas_Guilliams_2022_cell" = "Liver",
                   "FBM_Jardine_2021_Nature" = "Bone Marrow and blood",
                   "Kamath_2022_normal" = "Brain",
                   "CARE" = "Heart",
                   "HLCA_core_healthy_LP" = "Lung",
                   "Mouse" = "Atlas - Mouse",
                   "Human" = "Atlas - Human")

# Assign the organ values based on the study column
add_MG$organ <- organ_mapping[add_MG$Dataset]

add_MG_atlas = add_MG%>%filter(Dataset%in%c("Human","Mouse"))
add_MG_organ = add_MG%>%filter(!Dataset%in%c("Human","Mouse"))



cepo_s_MG_tms=cepo_s_MG%>%filter(Dataset=="ts_pc")  #107 CT in tms; 157 CT in ts.
sclinker_s_MG_tms=sclinker_s_MG%>%filter(Dataset=="ts_pc") #36 CT in tms; 40 CT in ts.
sort(unique(sclinker_s_MG_tms$FULL_NAME))
sort(unique(cepo_s_MG_tms$FULL_NAME))


cepo_s_MG_smille=cepo_s_MG%>%filter(Dataset=="FBM_Jardine_2021_Nature")
sclinker_s_MG_smille=sclinker_s_MG%>%filter(Dataset=="FBM_Jardine_2021_Nature")

sort(unique(sclinker_s_MG_smille$FULL_NAME))
sort(unique(cepo_s_MG_smille$FULL_NAME))


summary1 <- cepo_s_MG  %>%
  group_by(Dataset, Metrics,gene_group) %>%
  summarise(Count = n(), .groups = 'drop') 

summary2 <- sclinker_s_MG  %>%
  group_by(Dataset, Metrics,gene_group) %>%
  summarise(Count = n(), .groups = 'drop') 
summary1
summary2
```

# MGset-con organ two-side [Not use]
```{r}
library(ggplot2)
library(data.table)
library(dplyr)
library(readxl)

conMGset_organ_df=fread("/Users/angox/Downloads/Manuscripts/Benchmark/All_organ_8metrics_MAGMAgeneset_continuous_twoside_results.txt")

conMGset_organ_df <- conMGset_organ_df %>% mutate(gene_group = ifelse(grepl("_pc$", Dataset), "PCgene", "allgene"))
conMGset_organ_df$Dataset=gsub("_expr_gene","",conMGset_organ_df$Dataset)
conMGset_organ_df$Dataset=gsub("_pc","",conMGset_organ_df$Dataset)
conMGset_organ_df$Dataset=gsub("_withPos","",conMGset_organ_df$Dataset)
conMGset_organ_df$Dataset[conMGset_organ_df$Dataset == "Cheng_2018_Cell_Reports"] <- "Cheng_2018_Cell_Reports_updated"

conMGset_organ_df_tmp = inner_join(conMGset_organ_df%>%dplyr::rename(file=Trait),Trait_dt%>%select(Phenotype,file)) %>% select(!c("file")) # 38 traits

pattern_replacements <- c(
   "esmu" = "CELLECT-ESμ",
  "ges_esw" = "CELLECT-GES",
  "det_esw" = "CELLECT-DET",
  "nsi_esw" = "CELLECT-NSI",
  "ep_esw" = "CELLECT-EP",
  "cepo_norm" = "Cepo"
)

# Apply the replacements to metrics names
conMGset_organ_df_tmp <- conMGset_organ_df_tmp %>%
  mutate(Metrics = sapply(Metrics, function(x) {
    for (pattern in names(pattern_replacements)) {
      x <- gsub(pattern, pattern_replacements[pattern], x)
    }
    return(x)
  })) 



conMG_organ_two <- conMGset_organ_df_tmp %>%
  mutate(FULL_NAME = case_when(
    Metrics %in% c("Cepo", "sclinker") & Dataset == "HLCA_core_healthy_LP" & FULL_NAME == "CD8_positive__alpha_beta_T_cell" ~ "CD8.positive__alpha.beta_T_cell",
    Metrics %in% c("Cepo", "sclinker") & Dataset == "HLCA_core_healthy_LP" & FULL_NAME == "CD4_positive__alpha_beta_T_cell" ~ "CD4.positive__alpha.beta_T_cell",
    TRUE ~ FULL_NAME  # Keep all other values unchanged
  ))%>%
  mutate(FULL_NAME = case_when(
   Dataset == "HLCA_core_healthy_LP" & FULL_NAME == "CD8-positive__alpha-beta_T_cell" ~ "CD8.positive__alpha.beta_T_cell",
   Dataset == "HLCA_core_healthy_LP" & FULL_NAME == "CD4-positive__alpha-beta_T_cell" ~ "CD4.positive__alpha.beta_T_cell",
    TRUE ~ FULL_NAME  # Keep all other values unchanged
  )) %>% dplyr::rename(CT_ldsc="FULL_NAME")



organ_mapping <- c("Cheng_2018_Cell_Reports_updated" = "Skin",
                   "Fasolino_2022_Nat_Metab_normal_only" = "Pancreas",
                   "2019_Smillie_normal_cellxgene" = "Colon",
                   "human_liver_atlas_Guilliams_2022_cell" = "Liver",
                   "FBM_Jardine_2021_Nature" = "Bone Marrow and blood",
                   "Kamath_2022_normal" = "Brain",
                   "CARE" = "Heart",
                   "HLCA_core_healthy_LP" = "Lung")

# Assign the organ values based on the study column
conMG_organ_two$organ <- organ_mapping[conMG_organ_two$Dataset]



conMG_organ_two = inner_join(conMG_organ_two, Trait_dt2%>%select(Phenotype,CT_ldsc,CT_fig,Dataset,Property)) %>% mutate(CT_Pheno = paste(CT_fig, Phenotype, sep = "_"), Annotation="Continuous-two-side")


summary1 <- conMG_organ_two  %>%
  group_by(Dataset, Property, Metrics,gene_group) %>%
  summarise(Count = n(), .groups = 'drop') %>%
  pivot_wider(names_from = Property, values_from = Count, values_fill = 0)

print(summary1)


summary2 <- conMG_organ_two  %>%
  group_by(Property, Metrics,gene_group) %>%
  summarise(Count = n(), .groups = 'drop') %>%
  pivot_wider(names_from = Property, values_from = Count, values_fill = 0)

print(summary2)

```

# MGset-con organ one side
```{r}

library(ggplot2)
library(data.table)
library(dplyr)
library(readxl)

conMGset_organ_df=fread("/Users/angox/Downloads/Manuscripts/Benchmark/All_organ_8metrics_MAGMAgeneset_continuous_oneside_results.txt")

conMGset_organ_df <- conMGset_organ_df %>% mutate(gene_group = ifelse(grepl("_pc$", Dataset), "PCgene", "allgene"))
conMGset_organ_df$Dataset=gsub("_expr_gene","",conMGset_organ_df$Dataset)
conMGset_organ_df$Dataset=gsub("_pc","",conMGset_organ_df$Dataset)
conMGset_organ_df$Dataset=gsub("_withPos","",conMGset_organ_df$Dataset)
conMGset_organ_df$Dataset[conMGset_organ_df$Dataset == "Cheng_2018_Cell_Reports"] <- "Cheng_2018_Cell_Reports_updated"

conMGset_organ_df_tmp = inner_join(conMGset_organ_df%>%dplyr::rename(file=Trait),Trait_dt%>%select(Phenotype,file)) %>% select(!c("file")) # 38 traits

pattern_replacements <- c(
   "esmu" = "CELLECT-ESμ",
  "ges_esw" = "CELLECT-GES",
  "det_esw" = "CELLECT-DET",
  "nsi_esw" = "CELLECT-NSI",
  "ep_esw" = "CELLECT-EP",
  "cepo_norm" = "Cepo"
)

# Apply the replacements to metrics names
conMGset_organ_df_tmp <- conMGset_organ_df_tmp %>%
  mutate(Metrics = sapply(Metrics, function(x) {
    for (pattern in names(pattern_replacements)) {
      x <- gsub(pattern, pattern_replacements[pattern], x)
    }
    return(x)
  })) 



conMG_organ <- conMGset_organ_df_tmp %>%
  mutate(FULL_NAME = case_when(
    Metrics %in% c("Cepo", "sclinker") & Dataset == "HLCA_core_healthy_LP" & FULL_NAME == "CD8_positive__alpha_beta_T_cell" ~ "CD8.positive__alpha.beta_T_cell",
    Metrics %in% c("Cepo", "sclinker") & Dataset == "HLCA_core_healthy_LP" & FULL_NAME == "CD4_positive__alpha_beta_T_cell" ~ "CD4.positive__alpha.beta_T_cell",
    TRUE ~ FULL_NAME  # Keep all other values unchanged
  ))%>%
  mutate(FULL_NAME = case_when(
   Dataset == "HLCA_core_healthy_LP" & FULL_NAME == "CD8-positive__alpha-beta_T_cell" ~ "CD8.positive__alpha.beta_T_cell",
   Dataset == "HLCA_core_healthy_LP" & FULL_NAME == "CD4-positive__alpha-beta_T_cell" ~ "CD4.positive__alpha.beta_T_cell",
    TRUE ~ FULL_NAME  # Keep all other values unchanged
  )) %>% dplyr::rename(CT_ldsc="FULL_NAME")



organ_mapping <- c("Cheng_2018_Cell_Reports_updated" = "Skin",
                   "Fasolino_2022_Nat_Metab_normal_only" = "Pancreas",
                   "2019_Smillie_normal_cellxgene" = "Colon",
                   "human_liver_atlas_Guilliams_2022_cell" = "Liver",
                   "FBM_Jardine_2021_Nature" = "Bone Marrow and blood",
                   "Kamath_2022_normal" = "Brain",
                   "CARE" = "Heart",
                   "HLCA_core_healthy_LP" = "Lung")

# Assign the organ values based on the study column
conMG_organ$organ <- organ_mapping[conMG_organ$Dataset]

conMG_organ = inner_join(conMG_organ, Trait_dt2%>%select(Phenotype,CT_ldsc,CT_fig,Dataset,Property)) %>% mutate(CT_Pheno = paste(CT_fig, Phenotype, sep = "_"), Annotation="Continuous-one-side")

summary1 <- conMG_organ  %>%
  group_by(Dataset, Property, Metrics,gene_group) %>%
  summarise(Count = n(), .groups = 'drop') %>%
  pivot_wider(names_from = Property, values_from = Count, values_fill = 0)

print(summary1)


summary2 <- conMG_organ  %>%
  group_by(Property, Metrics,gene_group) %>%
  summarise(Count = n(), .groups = 'drop') %>%
  pivot_wider(names_from = Property, values_from = Count, values_fill = 0)

print(summary2)


```


# MGset-bi organ all genes
```{r}

library(data.table)
library(dplyr)
library(readxl)

MGset_organ_df=fread("/Users/angox/Downloads/Manuscripts/Benchmark/All_organ_CT_allgenes_8metrics_MAGMAgeneset_results.txt")

# Standardize the study names to match s_table2
MGset_organ_df$Dataset=gsub("ctd_","",MGset_organ_df$Dataset)
MGset_organ_df$Dataset=gsub("_expr_gene","",MGset_organ_df$Dataset)
MGset_organ_df$Dataset=gsub("_allgenes","",MGset_organ_df$Dataset)
MGset_organ_df$Dataset[MGset_organ_df$Dataset == "HLCA_core_healthy"] <- "HLCA_core_healthy_LP"

MGset_organ_df_tmp = inner_join(MGset_organ_df%>%dplyr::rename(file=Trait),Trait_dt%>%select(Phenotype,file)) %>% select(!c("file")) # 38 traits

pattern_replacements <- c(
  "esmu" = "CELLECT-ESμ",
  "ges.esw" = "CELLECT-GES",
  "det.esw" = "CELLECT-DET",
  "nsi.esw" = "CELLECT-NSI",
  "ep.esw" = "CELLECT-EP",
  "cepo_norm" = "Cepo"
)

# Apply the replacements to metrics names
MGset_organ_df_tmp <- MGset_organ_df_tmp %>%
  mutate(Metrics = sapply(Metrics, function(x) {
    for (pattern in names(pattern_replacements)) {
      x <- gsub(pattern, pattern_replacements[pattern], x)
    }
    return(x)
  })) 


MG_organ_set_allgenes <- MGset_organ_df_tmp %>%
  mutate(FULL_NAME = case_when(
    Metrics %in% c("Cepo", "sclinker") & Dataset == "HLCA_core_healthy_LP" & FULL_NAME == "CD8_positive__alpha_beta_T_cell" ~ "CD8.positive__alpha.beta_T_cell",
    Metrics %in% c("Cepo", "sclinker") & Dataset == "HLCA_core_healthy_LP" & FULL_NAME == "CD4_positive__alpha_beta_T_cell" ~ "CD4.positive__alpha.beta_T_cell",
    TRUE ~ FULL_NAME  # Keep all other values unchanged
  ))%>%dplyr::rename(CT_ldsc="FULL_NAME")

organ_mapping <- c("Cheng_2018_Cell_Reports_updated" = "Skin",
                   "Fasolino_2022_Nat_Metab_normal_only" = "Pancreas",
                   "2019_Smillie_normal_cellxgene" = "Colon",
                   "human_liver_atlas_Guilliams_2022_cell" = "Liver",
                   "FBM_Jardine_2021_Nature" = "Bone Marrow and blood",
                   "Kamath_2022_normal" = "Brain",
                   "CARE" = "Heart",
                   "HLCA_core_healthy_LP" = "Lung")

# Assign the organ values based on the study column
MG_organ_set_allgenes$organ <- organ_mapping[MG_organ_set_allgenes$Dataset]


MGset_organ_allgenes = inner_join(MG_organ_set_allgenes, Trait_dt2%>%select(Phenotype,CT_ldsc,CT_fig,Dataset,Property)) %>% mutate(CT_Pheno = paste(CT_fig, Phenotype, sep = "_"), Annotation="Binary-one-side") 

MGset_organ_allgenes$Method[MGset_organ_allgenes$Dataset == "MAGMA gene-set"] <- "MAGMA set binary one side"

summary1 <- MGset_organ_allgenes  %>%
  group_by(Dataset, Property, Metrics) %>%
  summarise(Count = n(), .groups = 'drop') %>%
  pivot_wider(names_from = Property, values_from = Count, values_fill = 0)

print(summary1)


summary2 <- MGset_organ_allgenes  %>%
  group_by(Property, Metrics) %>%
  summarise(Count = n(), .groups = 'drop') %>%
  pivot_wider(names_from = Property, values_from = Count, values_fill = 0)

print(summary2)


```


# MGset organ PC
```{r}
MGset_organ_df=fread("/Users/angox/Downloads/Manuscripts/Benchmark/All_organ_CT_PC_8metrics_MAGMAgeneset_results.txt")

# Standardize the study names to match s_table2
MGset_organ_df$Dataset=gsub("_pc","",MGset_organ_df$Dataset)
MGset_organ_df$Dataset=gsub("ctd_","",MGset_organ_df$Dataset)

MGset_organ_df$Dataset[MGset_organ_df$Dataset == "HLCA_core_healthy"] <- "HLCA_core_healthy_LP"
MGset_organ_df$Dataset[MGset_organ_df$Dataset == "Cheng_2018_Cell_Reports"] <- "Cheng_2018_Cell_Reports_updated"

MGset_organ_df_tmp = inner_join(MGset_organ_df%>%dplyr::rename(file=Trait),Trait_dt%>%select(Phenotype,file)) %>% select(!c("file")) # 38 traits

pattern_replacements <- c(
  "esmu" = "CELLECT-ESμ",
  "ges.esw" = "CELLECT-GES",
  "det.esw" = "CELLECT-DET",
  "nsi.esw" = "CELLECT-NSI",
  "ep.esw" = "CELLECT-EP",
  "cepo_norm" = "Cepo"
)


# Apply the replacements to metrics names
MGset_organ_df_tmp <- MGset_organ_df_tmp %>%
  mutate(Metrics = sapply(Metrics, function(x) {
    for (pattern in names(pattern_replacements)) {
      x <- gsub(pattern, pattern_replacements[pattern], x)
    }
    return(x)
  })) 


MG_organ_set_PCgenes <- MGset_organ_df_tmp %>%
  mutate(FULL_NAME = case_when(
    Metrics %in% c("Cepo", "sclinker") & Dataset == "HLCA_core_healthy_LP" & FULL_NAME == "CD8_positive__alpha_beta_T_cell" ~ "CD8.positive__alpha.beta_T_cell",
    Metrics %in% c("Cepo", "sclinker") & Dataset == "HLCA_core_healthy_LP" & FULL_NAME == "CD4_positive__alpha_beta_T_cell" ~ "CD4.positive__alpha.beta_T_cell",
    TRUE ~ FULL_NAME  # Keep all other values unchanged
  ))%>%dplyr::rename(CT_ldsc="FULL_NAME")

organ_mapping <- c("Cheng_2018_Cell_Reports_updated" = "Skin",
                   "Fasolino_2022_Nat_Metab_normal_only" = "Pancreas",
                   "2019_Smillie_normal_cellxgene" = "Colon",
                   "human_liver_atlas_Guilliams_2022_cell" = "Liver",
                   "FBM_Jardine_2021_Nature" = "Bone Marrow and blood",
                   "Kamath_2022_normal" = "Brain",
                   "CARE" = "Heart",
                   "HLCA_core_healthy_LP" = "Lung")

# Assign the organ values based on the study column
MG_organ_set_PCgenes$organ <- organ_mapping[MG_organ_set_PCgenes$Dataset]


MGset_organ_pc = inner_join(MG_organ_set_PCgenes, Trait_dt2%>%select(Phenotype,CT_ldsc,CT_fig,Dataset,Property)) %>% mutate(CT_Pheno = paste(CT_fig, Phenotype, sep = "_"), Annotation="Binary-one-side") 

MGset_organ_pc$Method[MGset_organ_pc$Dataset == "MAGMA gene-set"] <- "MAGMA set binary one side"


summary1 <- MGset_organ_pc  %>%
  group_by(Dataset, Property, Metrics) %>%
  summarise(Count = n(), .groups = 'drop') %>%
  pivot_wider(names_from = Property, values_from = Count, values_fill = 0)

print(summary1)


summary2 <- MGset_organ_pc  %>%
  group_by(Property, Metrics) %>%
  summarise(Count = n(), .groups = 'drop') %>%
  pivot_wider(names_from = Property, values_from = Count, values_fill = 0)

print(summary2)


```


# con-MGset atlas
```{r}
conMGset_atlas_df=fread("/Users/angox/Downloads/Manuscripts/Benchmark/Atlas_PC_8metrics_MAGMAgeneset_continuous_oneside_results.txt")
conMGset_atlas_df$Dataset <- ifelse(conMGset_atlas_df$Dataset == "ts_pc", "Human", ifelse(conMGset_atlas_df$Dataset == "tms_pc", "Mouse", conMGset_atlas_df$Dataset))
conMGset_atlas_df_tmp = inner_join(conMGset_atlas_df%>%dplyr::rename(file=Trait),Trait_dt%>%select(Phenotype,file)) %>% select(!c("file")) # 38 traits
pattern_replacements <- c(
  "esmu" = "CELLECT-ESμ",
  "ges.esw" = "CELLECT-GES",
  "det.esw" = "CELLECT-DET",
  "nsi.esw" = "CELLECT-NSI",
  "ep.esw" = "CELLECT-EP",
  "cepo_norm" = "Cepo"
)

# Apply the replacements to metrics names
conMGset_atlas_df_tmp <- conMGset_atlas_df_tmp %>%
  mutate(Metrics = sapply(Metrics, function(x) {
    for (pattern in names(pattern_replacements)) {
      x <- gsub(pattern, pattern_replacements[pattern], x)
    }
    return(x)
  })) 

Trait_dt2$Dataset[Trait_dt2$Dataset == "TS"] <- "Human"
conMGset_atlas = inner_join(conMGset_atlas_df_tmp%>%dplyr::rename(CT_ldsc="FULL_NAME"), Trait_dt2%>%select(Phenotype,CT_ldsc,CT_fig,Dataset,Property)) %>% 
  mutate(CT_Pheno = paste(CT_fig, Phenotype, sep = "_"), Annotation="Continuous-one-side")


organ_mapping <- c("Mouse" = "Atlas - Mouse",
                   "Human" = "Atlas - Human")



conMGset_atlas$Metrics[conMGset_atlas$Metrics == "TDEP"] <- "EP"
summary1 <- conMGset_atlas  %>%
  group_by(Dataset, Property, Metrics) %>%
  summarise(Count = n(), .groups = 'drop') %>%
  pivot_wider(names_from = Property, values_from = Count, values_fill = 0)

print(summary1)

```


# bi-MGset atlas
```{r}
MGset_atlas_df=fread("/Users/angox/Downloads/Manuscripts/Benchmark/TMS_TS_PC_allCT_8metrics_MAGMAgeneset.txt")
MGset_atlas_df$Dataset <- ifelse(MGset_atlas_df$Dataset == "ts_pc", "Human", ifelse(MGset_atlas_df$Dataset == "tms_pc", "Mouse", MGset_atlas_df$Dataset))
MGset_atlas_df_tmp = inner_join(MGset_atlas_df%>%dplyr::rename(file=Trait),Trait_dt%>%select(Phenotype,file)) %>% select(!c("file")) # 38 traits
pattern_replacements <- c(
  "esmu" = "CELLECT-ESμ",
  "ges.esw" = "CELLECT-GES",
  "det.esw" = "CELLECT-DET",
  "nsi.esw" = "CELLECT-NSI",
  "ep.esw" = "CELLECT-EP",
  "cepo_norm" = "Cepo"
)

# Apply the replacements to metrics names
MGset_atlas_df_tmp <- MGset_atlas_df_tmp %>%
  mutate(Metrics = sapply(Metrics, function(x) {
    for (pattern in names(pattern_replacements)) {
      x <- gsub(pattern, pattern_replacements[pattern], x)
    }
    return(x)
  })) 


biMGset_atlas = inner_join(MGset_atlas_df_tmp%>%dplyr::rename(CT_ldsc="FULL_NAME"), Trait_dt2%>%select(Phenotype,CT_ldsc,CT_fig,Dataset,Property)) %>% mutate(CT_Pheno = paste(CT_fig, Phenotype, sep = "_"), Annotation="Binary-one-side") %>%select(!c("gene_group"))
biMGset_atlas$Method[biMGset_atlas$Dataset == "MAGMA gene-set"] <- "MAGMA set binary one side"

summary1 <- biMGset_atlas  %>%
  group_by(Dataset, Property, Metrics) %>%
  summarise(Count = n(), .groups = 'drop') %>%
  pivot_wider(names_from = Property, values_from = Count, values_fill = 0)

print(summary1)

```
sclinker-human: causal 少1:
cat /scratch/user/uqali4/geneset_res/PCgenes_background/ts_pc/det.esw_s/MAGMA_100kb_based/ADHD_meta_Jan2022_iPSYCH1_iPSYCH2_deCODE_PGC.meta_tidy.ma.log
WARNING: analysis failed for 'erythrocyte' (set); could not invert variable design matrix: variable is collinear with conditioned covariates
sclinker-mouse: causal 少3


# Compare Metrics in organ:
# Conclusion: Use PC genes
```{r}
library(ggplot2)

biMGset_organ=rbind(MGset_organ_pc,MGset_organ_allgenes)
MGset_organ=rbind(rbind(biMGset_organ,conMG_organ,conMG_organ_two))

save(MGset_organ, file = "/Users/angox/Documents/Projects/Benchmark/single_organ_MGset_pairs_tmp_missHaircolor.RData")

# Filter data based on P < 0.05
filtered_data <- MGset_organ %>% filter(P < 0.05)  

Main_01 = ggplot(filtered_data%>%filter(!Property=="Resultant"), aes(x = Metrics, fill=factor(Annotation))) +
  geom_bar(position = "dodge") +
  facet_grid(Property~gene_group)+
  labs(
    title = "Counts of the pairs with P < 0.05",
    x = "Method",
    y = "Counts"
  ) + theme_minimal() +
  theme(
        axis.text.x = element_text(face = "bold", angle = 90, hjust = 1),
        text = element_text(size = 12),
        strip.text = element_text(color="black",size = 12, face = "bold"), 
        panel.border = element_rect(fill=NA,color="black", size=1, linetype="solid")) +
  xlab("") +
  scale_fill_brewer(palette = "Set1") +
   geom_hline(yintercept = 34*0.05, linetype="dotted",color = "red", size=0.5)+
   geom_hline(yintercept = 48, linetype="dotted",color = "red", size=0.5)
Main_01

Main_04 <- ggplot(
  MGset_organ %>% filter(!Property == "Resultant"),
  aes(x = Metrics, y = -log10(P), fill = factor(Annotation))
) +
  geom_violin() +
  stat_summary(
    fun = mean, geom = "point", shape = 20, size = 3, color = "black",
    position = position_dodge(width = 0.9)
  ) +
  facet_grid(Property ~ gene_group) + #, scales = "free_y"
  labs(
    x = "",
    y = "-log10-P",
    fill = NULL  # Remove legend title for fill aesthetic
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(
      angle = 45, hjust = 1, color = "black", size = 12, face = "bold"
    ),
    text = element_text(size = 12),
    axis.text.y = element_text(color = "black", size = 12, face = "bold"),
    strip.text = element_text(color = "black", size = 12, face = "bold"),
    panel.border = element_rect(
      fill = NA, color = "black", size = 1, linetype = "solid"
    ),
    legend.position = "top"
  ) +
  xlab("") +
  scale_fill_brewer(palette = "Set1") +
  geom_hline(
    yintercept = -log10(0.05), linetype = "dotted", color = "red", size = 0.5
  )

Main_04
# MG.metrics.gene.group.pdf

```

# No use!!!
```{r}
LDSC_organ$Method="con-LDSC"
organ_res_LD=rbind(LDSC_organ,MGset_organ%>%mutate(Annotation="Continuous")%>%select(names(LDSC_organ)))

filtered_data <- organ_res_LD %>% filter(P < 0.05)  

Main_0122 = ggplot(filtered_data%>%filter(!Property=="Resultant")%>%filter(Annotation=="Continuous"), aes(x = Metrics, fill=factor(Method))) +
  geom_bar(position = "dodge") +
  facet_grid(Property~gene_group)+
  labs(
    title = "Counts of the pairs with P < 0.05",
    x = "Method",
    y = "Counts"
  ) + theme_minimal() +
  theme(
        axis.text.x = element_text(face = "bold", angle = 90, hjust = 1),
        text = element_text(size = 12),
        strip.text = element_text(color="black",size = 12, face = "bold"), 
        panel.border = element_rect(fill=NA,color="black", size=1, linetype="solid")) +
  xlab("") +
  scale_fill_brewer(palette = "Set1") +
   geom_hline(yintercept = 33*0.05, linetype="dotted",color = "red", size=0.5)+
   geom_hline(yintercept = 48, linetype="dotted",color = "red", size=0.5)
Main_0122

```

# Compare Metrics in atlas
```{r}
MGset_atlas = rbind(biMGset_atlas,conMGset_atlas)

filtered_data_human <- MGset_atlas %>% filter(P < 0.05)   #%>%filter(Dataset=="Human") 

Main_01 = ggplot(filtered_data_human%>%filter(!Property=="Resultant"), aes(x = Metrics, fill=factor(Annotation))) +
  geom_bar(position = "dodge") +
  facet_grid(Property~Dataset)+
  labs(
    title = "Counts of the pairs with P < 0.05",
    x = "Method",
    y = "Counts",
    fill = "Annotation"
  ) + theme_minimal() +
  theme(
        axis.text.x = element_text(face = "bold", angle = 90, hjust = 1),
        text = element_text(size = 12),
        strip.text = element_text(color="black",size = 12, face = "bold"), 
        panel.border = element_rect(fill=NA,color="black", size=1, linetype="solid")) +
  xlab("") +
  scale_fill_brewer(palette = "Set2") +
   geom_hline(yintercept = 29*0.05, linetype="dotted",color = "red", size=0.5)+
  geom_hline(yintercept = 29, linetype="dotted",color = "red", size=0.5)
Main_01

 # Group by CT_Pheno and check for the presence of both "Human" and "Mouse"
#MGset_atlas <- MGset_atlas %>%
#  group_by(CT_Pheno) %>%
#  filter(all(c("Human", "Mouse") %in% Dataset)) %>%
#  ungroup()


# Filter data based on P < 0.05
filtered_data <- MGset_atlas %>% filter(P < 0.05)  
#%>%filter(Dataset=="Human")
Main_01 = ggplot(filtered_data%>%filter(!Property=="Resultant"), aes(x = Metrics, fill=factor(Dataset))) +
  geom_bar(position = "dodge") +
  facet_grid(Property~Annotation)+
  labs(
    title = "Counts of the pairs with P < 0.05",
    x = "Method",
    y = "Counts"
  ) + theme_minimal() +
  theme(
        axis.text.x = element_text(face = "bold", angle = 90, hjust = 1),
        text = element_text(size = 12),
        strip.text = element_text(color="black",size = 12, face = "bold"), 
        panel.border = element_rect(fill=NA,color="black", size=1, linetype="solid")) +
  xlab("") +
  scale_fill_brewer(palette = "Paired") +
  geom_hline(yintercept = 27*0.05, linetype="dotted",color = "red", size=0.5)+
  geom_hline(yintercept = 27, linetype="dotted",color = "red", size=0.5)
Main_01


```










