---
output:
  html_document: default
  pdf_document: default
---
# Figure for scDRS

save(organ_merged_scdrs, file = "/Users/angox/Downloads/Manuscripts/Benchmark/Data_draw_fig/single_organ_scDRS.RData")

# scDRS results, atlas results
# save(scDRS_all, file = "/Users/angox/Downloads/Manuscripts/Benchmark/Data_draw_fig/ts_tms_scDRS.RData")

# Check the number of control and causal pairs.
```{r}
library(ggplot2)
library(dplyr)
library(tidyr)
library(readxl)


file_path <- "/Users/angox/Downloads/Manuscripts/Benchmark_list.xlsx"
Trait_dt <- read_excel(file_path, sheet = "Pairs-Trait")%>%select(Phenotype,file,conldsc_file)
head(Trait_dt)

file_path <- "/Users/angox/Downloads/Manuscripts/Benchmark/Results/S_table2.xlsx"
Trait_dt2 <- read_excel(file_path, sheet = "Cell_type_candidates")%>%dplyr::rename(Chategory=`Chategory [Follow by Phenotype]`)%>%select(c("Synonym","CT_scDRS","CT_cellect","CT_ldsc","Dataset","CT_fig" , "Phenotype" ,"Property","Chategory"))%>% filter(!Chategory=="Special")
head(Trait_dt2)

Trait_dt2$Dataset <- ifelse(Trait_dt2$Dataset == "TS", "Human", ifelse(Trait_dt2$Dataset == "TMS", "Mouse", Trait_dt2$Dataset))


phenotype_comparison3 <- Trait_dt2 %>%
  mutate(CT_Pheno = paste(CT_fig, Phenotype, sep = "_")) %>%
  filter(Property=="Control") %>%
  group_by(Dataset, CT_Pheno) %>%
  summarise(Count = n(), .groups = 'drop') %>%
  pivot_wider(names_from = Dataset, values_from = Count, values_fill = 0)

# summary table
print(phenotype_comparison3)


# Create a summary table to compare the count of Phenotypes in "Control" and "Causal"
phenotype_comparison <- Trait_dt2 %>%
  mutate(CT_Pheno = paste(CT_fig, Phenotype, sep = "_")) %>%
  group_by(CT_Pheno, Dataset, Property) %>%
  summarise(Count = n(), .groups = 'drop') %>%
  pivot_wider(names_from = Property, values_from = Count, values_fill = 0)

print(phenotype_comparison)

phenotype_comparison2 <- Trait_dt2 %>%
  mutate(CT_Pheno = paste(CT_fig, Phenotype, sep = "_")) %>%
  group_by(Dataset, Property) %>%
  summarise(Count = n(), .groups = 'drop') %>%
  pivot_wider(names_from = Property, values_from = Count, values_fill = 0)

# Assuming your data is stored in a tibble called phenotype_comparison2
phenotype_comparison2 <- phenotype_comparison2 %>%
  mutate(type = ifelse(Dataset %in% c("Human", "Mouse"), "Atlas", "Single_organ"))

print(phenotype_comparison2)


# sum up the 'Causal' and 'Control' for each 'type'
summary_table <- phenotype_comparison2 %>%
  group_by(type) %>%
  summarise(
    total_causal = sum(Causal),
    total_control = sum(Control)
  )

print(summary_table)

```


# Merge with CT-Trait property pairs
```{r}
library(data.table)
library(dplyr)
library(tidyr)
library(readxl)
load("/Users/angox/Downloads/Manuscripts/Benchmark/Data_draw_fig/ts_tms_scDRS.RData")
load("/Users/angox/Downloads/Manuscripts/Benchmark/Data_draw_fig/single_organ_scDRS.RData")
scDRS_atlas_pair = inner_join(scDRS_all%>%mutate(statistic_P=2*pnorm(-abs(assoc_mcz))),Trait_dt2%>%select(Phenotype,CT_scDRS,CT_fig,Dataset,Property)) 

scDRS_organ_pair = inner_join(organ_merged_scdrs%>%mutate(statistic_P=2*pnorm(-abs(assoc_mcz))),Trait_dt2%>%select(Phenotype,CT_scDRS,CT_fig,Dataset,Property))


summary_scDRS_organ <- scDRS_organ_pair %>%
  mutate(CT_Pheno = paste(CT_fig, Phenotype, sep = "_")) %>%
  group_by(gene_group,organ, Property,Strategy) %>%
  summarise(Count = n(), .groups = 'drop') %>%
  pivot_wider(names_from = Property, values_from = Count, values_fill = 0)

print(summary_scDRS_organ)

# Filter data for the Lung organ and both strategies
lung_data <- scDRS_organ_pair %>%
  filter(organ == "Lung" & Strategy %in% c("MAGMA window 10kb", "mBAT-combo window 10kb"))

# Group by CT_Pheno and Strategy to identify missing entries
comparison <- lung_data %>%
  mutate(CT_Pheno = paste(CT_fig, Phenotype, sep = "_")) %>%
  group_by(CT_Pheno, Strategy) %>%
  summarise(Count = n(), .groups = 'drop') %>%
  pivot_wider(names_from = Strategy, values_from = Count, values_fill = 0)

# Print out the comparison table to identify missing CT_Pheno
print(comparison)

```

# Atlas results
```{r}

summary <- scDRS_atlas_pair %>%
  mutate(CT_Pheno = paste(CT_fig, Phenotype, sep = "_")) %>%
  group_by(Dataset, Property, Strategy) %>%
  summarise(Count = n(), .groups = 'drop') %>%
  pivot_wider(names_from = Property, values_from = Count, values_fill = 0)

print(summary)


# Filter data based on assoc_mcp < 0.05
filtered_data <- scDRS_atlas_pair%>%filter(!Property=="Resultant") %>% filter(statistic_P < 0.05)  #statistic_P
#save(filtered_data, file = "/Users/angox/Downloads/Manuscripts/Benchmark/Data_draw_fig/scdrs_atlas_controlpos_interesting.RData")
#
#%>%filter(Dataset=="Human")
Main_01=ggplot(filtered_data%>%filter(Dataset=="Human"), aes(x = Strategy, fill=factor(Strategy))) +
  geom_bar(position = "dodge") +
  facet_grid(.~Property)+
  #facet_wrap(Dataset~., scales = "free")+
  labs(
    title = "Counts of the pairs with statistic-P < 0.05",
    x = "Method",
    y = "Counts",
    fill = "Property"
  ) + theme_minimal() +
  theme(
        axis.text.x = element_text(face = "bold", angle = 15, hjust = 1),
        text = element_text(size = 12),
        strip.text = element_text(color="black",size = 12, face = "bold"), 
        panel.border = element_rect(fill=NA,color="black", size=1, linetype="solid")) +
  xlab("")  +
  scale_fill_manual(values = c("MAGMA window 10kb" = "#006600", "mBAT-combo window 10kb" = "#FF6600")) +
   geom_hline(yintercept = 29*0.05, linetype="dotted",color = "red", size=0.5) +
  ylim(0, 29)  # Set y-axis limits to a maximum of 28
Main_01

# Filter data based on assoc_mcp < 0.05
filtered_data.01 <- scDRS_atlas_pair%>%filter(!Property=="Resultant") %>% filter(assoc_mcp < 0.05) #%>%mutate(CT_trait=paste0(CT_fig,"_",Phenotype)) %>%select(assoc_mcp,CT_trait,Strategy,Dataset) #statistic_P
#
Main_01.01=ggplot(filtered_data.01%>%filter(Dataset=="Human"), aes(x = Strategy, fill=factor(Strategy))) +
  geom_bar(position = "dodge") +
  facet_grid(.~Property)+
  #facet_wrap(Dataset~., scales = "free")+
  labs(
    title = "Counts of the pairs with MC-P < 0.05",
    x = "Method",
    y = "Counts",
    fill = "Property"
  ) + theme_minimal() +
  theme(
        axis.text.x = element_text(face = "bold",colour = c("black","darkred"), angle = 15, hjust = 1),
        text = element_text(size = 13),
        strip.text = element_text(color="black",size = 13, face = "bold"), 
        panel.border = element_rect(fill=NA,color="black", size=1, linetype="solid")) +
  xlab("")  +
  scale_fill_manual(values = c("MAGMA window 10kb" = "#006600", "mBAT-combo window 10kb" = "#FF6600")) +
   geom_hline(yintercept = 29*0.05, linetype="dotted",color = "red", size=0.5) +
  ylim(0, 29)  # Set y-axis limits to a maximum of 28
Main_01.01


```


# Mouse vs. Human
```{r}

# Filter data based on assoc_mcp < 0.05
filtered_data_human <- scDRS_atlas_pair%>%filter(Dataset=="Human")%>% filter(!Property=="Resultant") %>% filter(assoc_mcp < 0.05) # %>%mutate(CT_trait=paste0(CT_fig,"_",Phenotype)) %>%select(assoc_mcp,CT_trait,Strategy,Dataset) 

Main_01.01=ggplot(filtered_data_human, aes(x = Strategy, fill=factor(Dataset))) +
  geom_bar(position = "dodge") +
  facet_grid(Property~Dataset)+
  labs(
    title = "Counts of the pairs with MC-P < 0.05",
    x = "Method",
    y = "Counts",
    fill = "Property"
  ) + theme_minimal() +
  theme(
        axis.text.x = element_text(face = "bold",colour = c("black","darkred"), angle = 15, hjust = 1),
        text = element_text(size = 13),
        strip.text = element_text(color="black",size = 13, face = "bold"), 
        panel.border = element_rect(fill=NA,color="black", size=1, linetype="solid")) +
  xlab("")  +
  scale_fill_manual(values = c("MAGMA window 10kb" = "#006600", "mBAT-combo window 10kb" = "#FF6600")) +
   geom_hline(yintercept = 29*0.05, linetype="dotted",color = "red", size=0.5) +
  ylim(0, 29)  # Set y-axis limits to a maximum of 28
Main_01.01


#  # Group by CT_Pheno and check for the presence of both "Human" and "Mouse"
scDRS_atlas_pair_filtered <- scDRS_atlas_pair %>%
  mutate(CT_Pheno = paste(CT_fig, Phenotype, sep = "_")) %>%
  group_by(CT_Pheno) %>%
  filter(all(c("Human", "Mouse") %in% Dataset)) %>%
  ungroup()

print(scDRS_atlas_pair_filtered)

summary01 <- scDRS_atlas_pair_filtered %>%
  group_by(Dataset, Property, Strategy) %>%
  summarise(Count = n(), .groups = 'drop') %>%
  pivot_wider(names_from = Property, values_from = Count, values_fill = 0)

print(summary01)


filtered_data <- scDRS_atlas_pair_filtered %>% filter(!Property=="Resultant") %>% filter(statistic_P < 0.05)  #statistic_P
filtered_data %>%
  group_by(Dataset, Property, Strategy) %>%
  summarise(Count = n(), .groups = 'drop') %>%
  pivot_wider(names_from = Property, values_from = Count, values_fill = 0)

Main_01 = ggplot(filtered_data, aes(x = Strategy, fill=factor(Dataset))) +
  geom_bar(position = "dodge") +
  facet_grid(Property~ .) +
  labs(
    title = "Counts of the pairs with statistic-P < 0.05",
    x = "Method",
    y = "Counts",
    fill = "Property"
  ) + theme_minimal() +
  theme(
        axis.text.x = element_text(face = "bold", angle = 15, hjust = 1),
        text = element_text(size = 12),
        strip.text = element_text(color="black",size = 12, face = "bold"), 
        panel.border = element_rect(fill=NA,color="black", size=1, linetype="solid")) +
  xlab("") +
  scale_fill_brewer(palette = "Paired") +
  geom_hline(yintercept = 26*0.05, linetype="dotted",color = "red", size=0.5) +
  ylim(0, 27)  # Set y-axis limits to a maximum of 27
Main_01

# Filter data based on assoc_mcp < 0.05
filtered_data.01 <- scDRS_atlas_pair_filtered %>% filter(!Property=="Resultant") %>% filter(assoc_mcp < 0.05) # %>%mutate(CT_trait=paste0(CT_fig,"_",Phenotype)) %>%select(assoc_mcp,CT_trait,Strategy,Dataset) #statistic_P
#

filtered_data.01 %>%
  group_by(Dataset, Property, Strategy) %>%
  summarise(Count = n(), .groups = 'drop') %>%
  pivot_wider(names_from = Property, values_from = Count, values_fill = 0)

Main_01.01=ggplot(filtered_data.01, aes(x = Strategy, fill=factor(Dataset))) +
  geom_bar(position = "dodge") +
  facet_grid(Property~ .) +
  labs(
    title = "Counts of the pairs with MC-P < 0.05",
    x = "Method",
    y = "Counts",
    fill = "Property"
  ) + theme_minimal() +
  theme(
        axis.text.x = element_text(face = "bold",colour = c("black","darkred"), angle = 15, hjust = 1),
        text = element_text(size = 13),
        strip.text = element_text(color="black",size = 13, face = "bold"), 
        panel.border = element_rect(fill=NA,color="black", size=1, linetype="solid")) +
  xlab("") +
  scale_fill_brewer(palette = "Paired") +
   geom_hline(yintercept = 26*0.05, linetype="dotted",color = "red", size=0.5) +
  ylim(0, 26)  # Set y-axis limits to a maximum of 26

Main_01.01


# Filter for mBAT-combo window 10kb strategy and Causal property
mouse_causal_MG <- filtered_data.01 %>%
  filter(Dataset == "Mouse" & Strategy == "MAGMA window 10kb" & Property == "Causal") %>%
  select(CT_Pheno) %>%
  distinct()

mouse_causal_MB <- filtered_data.01 %>%
  filter(Dataset == "Mouse" & Strategy == "mBAT-combo window 10kb" & Property == "Causal") %>%
  select(CT_Pheno) %>%
  distinct()

# Find what is in Human but not in Mouse
missing_in_mouse <- setdiff(mouse_causal_MG$CT_Pheno, mouse_causal_MB$CT_Pheno)

# Print the missing causal cell types for Mouse
print(missing_in_mouse)


```


> filtered_data%>%filter(Property=="Control",Strategy=="mBAT-combo window 10kb")%>%select(CT_Pheno)
# A tibble: 4 × 1
  CT_Pheno                                                     
  <chr>                                                        
1 tracheobronchial smooth muscle cell_Primary biliary cirrhosis
2 pancreatic polypeptide cell_Lymphocyte count                 
3 pancreatic polypeptide cell_Neutrophil count                 
4 tracheobronchial smooth muscle cell_Primary biliary cirrhosis


# Compare stat-P vs. MC-P in organ

```{r}
scDRS_organ_pair_comp=scDRS_organ_pair%>%mutate(CT_trait=paste0(CT_fig,"_",Phenotype))%>%filter(!Property=="Resultant")%>%select(gene_group,assoc_mcp,CT_trait,Strategy,organ,statistic_P,Property)

scDRS_atlas_pair_comp=scDRS_atlas_pair%>%mutate(CT_trait=paste0(CT_fig,"_",Phenotype))%>%filter(!Property=="Resultant")%>%select(assoc_mcp,CT_trait,Strategy,Dataset,statistic_P,Property)


pp=ggplot(scDRS_organ_pair_comp%>%filter(Strategy=="mBAT-combo window 10kb"), aes(x = -log10(statistic_P), y = -log10(assoc_mcp), color = Property)) +
  geom_point(size = 1, alpha = 0.7) +  
  facet_grid(gene_group~organ ) +                
  labs(
    x = "-log10(Statistic P)",                
    y = "-log10(Assoc MC-P)",                 
    title = "Assoc MC-P vs Statistic P (mBAT-combo) Faceted by Organ and gene group"
  ) +
  theme_minimal() +                    
  theme(
    text = element_text(size = 12),    
    strip.text = element_text(face = "bold"), 
    panel.border = element_rect(color = "black", fill = NA, size = 1)  
  ) +
  geom_hline(yintercept = -log10(0.05), linetype="dotted",color = "red", size=0.5)+
  geom_vline(xintercept = -log10(0.05), linetype="dotted",color = "red", size=0.5)  +
  scale_color_brewer(palette = "Set1")  

pp



pp1=ggplot(scDRS_organ_pair_comp%>%filter(Strategy=="mBAT-combo window 10kb"), aes(x = -log10(statistic_P), y = -log10(assoc_mcp), color = Property)) +
  geom_point(size = 1, alpha = 0.7) + 
  facet_wrap(~ gene_group) +              
  labs(
    x = "-log10(Statistic P)",             
    y = "-log10(Assoc MCP)",               
    title = "Assoc MC-P vs Statistic P (mBAT-combo) Faceted by gene group"
  ) +
  theme_minimal() +                    
  theme(
    text = element_text(size = 12),   
    strip.text = element_text(face = "bold"),  
    panel.border = element_rect(color = "black", fill = NA, size = 1)  
  ) +
  geom_hline(yintercept = -log10(0.05), linetype="dotted",color = "red", size=0.5)+
  geom_vline(xintercept = -log10(0.05), linetype="dotted",color = "red", size=0.5)  +
  scale_color_brewer(palette = "Set1") 

pp1



pp2=ggplot(scDRS_organ_pair_comp%>%filter(Strategy=="MAGMA window 10kb"), aes(x = -log10(statistic_P), y = -log10(assoc_mcp), color = Property)) +
  geom_point(size = 1, alpha = 0.7) + 
  facet_grid(gene_group~organ ) +                
  labs(
    x = "-log10(Statistic P)",              
    y = "-log10(Assoc MC-P)",                 
    title = "Assoc MC-P vs Statistic P (MAGMA) Faceted by gene group"
  ) +
  theme_minimal() +                    
  theme(
    text = element_text(size = 12),  
    strip.text = element_text(face = "bold"),  
    panel.border = element_rect(color = "black", fill = NA, size = 1) 
  ) +
  geom_hline(yintercept = -log10(0.05), linetype="dotted",color = "red", size=0.5)+
  geom_vline(xintercept = -log10(0.05), linetype="dotted",color = "red", size=0.5)  +
  scale_color_brewer(palette = "Set1")

pp2



pp12=ggplot(scDRS_organ_pair_comp%>%filter(Strategy=="MAGMA window 10kb"), aes(x = -log10(statistic_P), y = -log10(assoc_mcp), color = Property)) +
  geom_point(size = 1, alpha = 0.7) +  
  facet_wrap(~ gene_group) +               
  labs(
    x = "-log10(Statistic P)",               
    y = "-log10(Assoc MCP)",                  
    title = "Assoc MC-P vs Statistic P (MAGMA) Faceted by gene group"
  ) +
  theme_minimal() +                  
  theme(
    text = element_text(size = 12),    
    strip.text = element_text(face = "bold"),  
    panel.border = element_rect(color = "black", fill = NA, size = 1) 
  ) +
  geom_hline(yintercept = -log10(0.05), linetype="dotted",color = "red", size=0.5)+
  geom_vline(xintercept = -log10(0.05), linetype="dotted",color = "red", size=0.5)  +
  scale_color_brewer(palette = "Set1") 

pp12



pp22=ggplot(scDRS_organ_pair_comp%>%filter(gene_group=="allgene"), aes(x = -log10(statistic_P), y = -log10(assoc_mcp), color = Property)) +
  geom_point(size = 1, alpha = 0.7) +  
  facet_wrap(~ Strategy) +                
  labs(
    x = "-log10(Statistic P)",                
    y = "-log10(Assoc MCP)",                  
    title = "Assoc MC-P vs Statistic P (data expressed genes) Faceted by Method"
  ) +
  theme_minimal() +                   
  theme(
    text = element_text(size = 12),    
    strip.text = element_text(face = "bold"), 
    panel.border = element_rect(color = "black", fill = NA, size = 1)  
  ) +
  geom_hline(yintercept = -log10(0.05), linetype="dotted",color = "red", size=0.5)+
  geom_vline(xintercept = -log10(0.05), linetype="dotted",color = "red", size=0.5)  +
  scale_color_brewer(palette = "Set1") 

pp22


pp23=ggplot(scDRS_organ_pair_comp%>%filter(gene_group=="PCgene"), aes(x = -log10(statistic_P), y = -log10(assoc_mcp), color = Property)) +
  geom_point(size = 1, alpha = 0.7) +  
  facet_wrap(~ Strategy) +                
  labs(
    x = "-log10(Statistic P)",                
    y = "-log10(Assoc MCP)",                  
    title = "Assoc MC-P vs Statistic P (protein coding genes) Faceted by Method"
  ) +
  theme_minimal() +                    
  theme(
    text = element_text(size = 12),   
    strip.text = element_text(face = "bold"),  
    panel.border = element_rect(color = "black", fill = NA, size = 1)  
  ) +
  geom_hline(yintercept = -log10(0.05), linetype="dotted",color = "red", size=0.5)+
  geom_vline(xintercept = -log10(0.05), linetype="dotted",color = "red", size=0.5)  +
  scale_color_brewer(palette = "Set1")  

pp23
```


# Compare stat-P vs. MC-P in Atlas
```{r}

scDRS_atlas_pair_comp=scDRS_atlas_pair%>%mutate(CT_trait=paste0(CT_fig,"_",Phenotype))%>%filter(!Property=="Resultant")%>%select(assoc_mcp,CT_trait,Strategy,Dataset,statistic_P,Property)


pp33=ggplot(scDRS_atlas_pair_comp, aes(x = -log10(statistic_P), y = -log10(assoc_mcp), color = Property)) +
  geom_point(size = 1, alpha = 0.7) +  
  facet_grid(Dataset~ Strategy) +             
  labs(
    x = "-log10(Statistic P)",              
    y = "-log10(Assoc MCP)",                
    title = "Assoc MC-P vs Statistic P Faceted by Method and Species"
  ) +
  theme_minimal() +                   
  theme(
    text = element_text(size = 12),  
    strip.text = element_text(face = "bold"),  
    panel.border = element_rect(color = "black", fill = NA, size = 1) 
  ) +
  geom_hline(yintercept = -log10(0.05), linetype="dotted",color = "red", size=0.5)+
  geom_vline(xintercept = -log10(0.05), linetype="dotted",color = "red", size=0.5)  +
  scale_color_brewer(palette = "Set1")  

pp33

```




```{r}

summary2 <- scDRS_organ_pair %>%
  mutate(CT_Pheno = paste(CT_fig, Phenotype, sep = "_")) %>%
  group_by(Property,Strategy,gene_group) %>%
  summarise(Count = n(), .groups = 'drop') %>%
  pivot_wider(names_from = Property, values_from = Count, values_fill = 0)

print(summary2)

# Filter data based on assoc_mcp < 0.05
filtered_data <- scDRS_organ_pair%>%filter(!Property=="Resultant") %>% filter(statistic_P < 0.05)  #statistic_P
#save(filtered_data, file = "/Users/angox/Downloads/Manuscripts/Benchmark/Data_draw_fig/scdrs_atlas_controlpos_interesting.RData")
#%>%filter(!Property=="Resultant")
Main_01=ggplot(filtered_data, aes(x = gene_group, fill=factor(Strategy))) +
  geom_bar(position = "dodge") +
  facet_grid(.~Property)+
  #facet_wrap(Dataset~., scales = "free")+
  labs(
    title = "Counts of the pairs with statistic_P < 0.05",
    x = "Method",
    y = "Counts",
    fill = "Property"
  ) + theme_minimal() +
  theme(
        axis.text.x = element_text(face = "bold", angle = 15, hjust = 1),
        text = element_text(size = 12),
        strip.text = element_text(color="black",size = 12, face = "bold"), 
        panel.border = element_rect(fill=NA,color="black", size=1, linetype="solid")) +
  xlab("")  +
  scale_fill_manual(values = c("MAGMA window 10kb" = "#006600", "mBAT-combo window 10kb" = "#FF6600")) +
   geom_hline(yintercept = 33*0.05, linetype="dotted",color = "red", size=0.5)# +
 # ylim(0, 45)  # Set y-axis limits to a maximum of 28
Main_01

# Filter data based on assoc_mcp < 0.05
filtered_data.01 <- scDRS_organ_pair%>%filter(!Property=="Resultant")%>%filter(assoc_mcp < 0.05)#%>%mutate(CT_trait=paste0(CT_fig,"_",Phenotype)) %>%select(assoc_mcp,CT_trait,Strategy,Dataset) #statistic_P

Main_01.01=ggplot(filtered_data.01, aes(x = Strategy, fill=factor(gene_group))) +
  geom_bar(position = "dodge") +
  facet_grid(Property~gene_group)+
  #facet_wrap(Dataset~., scales = "free")+
  labs(
    title = "Counts of the pairs with MC-P < 0.05",
    x = "Method",
    y = "Counts",
    fill = "Gene Group"
  ) + theme_minimal() +
  theme(
        axis.text.x = element_text(face = "bold",colour = c("black","darkred"), angle = 45, hjust = 1),
        text = element_text(size = 13),
        strip.text = element_text(color="black",size = 13, face = "bold"), 
        panel.border = element_rect(fill=NA,color="black", size=1, linetype="solid")) +
  xlab("")  +
   geom_hline(yintercept = 33*0.05, linetype="dotted",color = "red", size=0.5)# +
 # ylim(0, 45)  # Set y-axis limits to a maximum of 28
#scale_fill_manual(values = c("MAGMA window 10kb" = "#006600", "mBAT-combo window 10kb" = "#FF6600")) +
Main_01.01

```
For the same cell type from different data sets.
# Draw figure using code in ~/Manuscript_Ang/Benchmark_comparison/Final_figure/Fig6.Atlas_vs_single_organ.Rmd
```{r}


f1=scDRS_atlas_pair%>%
  mutate(CT_Pheno = paste(CT_fig, Phenotype, sep = "_"),gene_group="PCgene",organ="Atlas")%>%filter(Dataset=="Human")%>%
  select(assoc_mcp,statistic_P, CT_fig, Phenotype, Property, Strategy, organ, CT_Pheno,n_cell,gene_group)

f2=scDRS_organ_pair%>%
  mutate(CT_Pheno = paste(CT_fig, Phenotype, sep = "_")) %>%
  select(assoc_mcp,statistic_P, CT_fig, Phenotype, Property, Strategy, organ, CT_Pheno,n_cell,gene_group)
vv=rbind(f1,f2)

# Keep only rows where CT_Pheno appears in both datasets
scDRS_common <- vv %>%
  semi_join(f1, by = "CT_Pheno") %>%
  semi_join(f2, by = "CT_Pheno")%>%filter(Strategy=="mBAT-combo window 10kb",gene_group=="PCgene")%>%filter(!Property=="Resultant")


# Create scatter plot comparing P values across different organs, faceted by Property
p1=ggplot(scDRS_common, aes(x = CT_Pheno, y = -log10(assoc_mcp), color = organ)) +
  geom_point(size = 1.5, alpha = 0.7) +  # Add points to represent P values
  facet_wrap(.~ Property, scales = "free_x") +  # Facet by Property
  labs(
    title = "Comparison of MC-P-values across different organs by mBAT-combo-scDRS, PC genes",
    x = "CT_Pheno",
    y = "-log10(P-value)",
    color = "Organ"
  ) +
  theme_minimal() +  # Apply minimal theme for clarity
  theme(
    panel.border = element_rect(fill=NA,color="black", size=1, linetype="solid"),
    text = element_text(size = 12),  # Adjust text size for readability
    strip.text = element_text(color = "black", size = 12, face = "bold"),  # Customize facet labels
    axis.text.x = element_text(angle = 90, hjust = 1)  # Rotate x-axis labels for better visibility
  ) +
  scale_color_brewer(palette = "Set1") +  # Use a color palette for the organs
   geom_hline(yintercept = -log10(0.05), linetype="dotted",color = "red", size=0.5)+
 ylim(0, 4)   # Log-transform the y-axis for better scaling of P-values

p1

p2=ggplot(scDRS_common, aes(x = CT_Pheno, y = -log10(statistic_P), color = organ)) +
  geom_point(size = 1.5, alpha = 0.7) +  # Add points to represent P values
  facet_wrap(~ Property, scales = "free_x") +  # Facet by Property
  labs(
    title = "Comparison of stat-P-values across different organs by mBAT-combo-scDRS, PC genes",
    x = "CT_Pheno",
    y = "-log10(P-value)",
    color = "Organ"
  ) +
  theme_minimal() +  # Apply minimal theme for clarity
  theme(
    legend.position = "left",
    panel.border = element_rect(fill=NA,color="black", size=1, linetype="solid"),
    text = element_text(color = "black", size = 12, face = "bold"),  # Adjust text size for readability
    strip.text = element_text(color = "black", size = 12, face = "bold"),  # Customize facet labels
    axis.text.x = element_text(angle = 40, hjust = 1,color = "black", size = 12, face = "bold")  # Rotate x-axis labels for better visibility
  ) +
  scale_color_brewer(palette = "Set1") +  # Use a color palette for the organs
   geom_hline(yintercept = -log10(0.05), linetype="dotted",color = "red", size=0.5)+
  xlab("")

p2
```



# Cell number and P

```{r}

p3=ggplot(scDRS_common %>%
         filter(Strategy == "mBAT-combo window 10kb") %>%
         filter(!Property == "Resultant"),
       aes(x = log10(n_cell), y = -log10(statistic_P), color = organ)) +
  geom_point(size = 1.5, alpha = 0.7) +  # Add points to represent P values
  geom_abline(intercept = 0, slope = 1, linetype = "dashed", color = "grey") +  # Add 45-degree line
  geom_smooth(method = "lm", se = FALSE, linetype = "solid", color = "black") +  # Add linear correlation line
  facet_wrap(~ Property, scales = "free_x") +  # Facet by Property
  labs(
    x = "log10(Cell number within Cell type)",
    y = "-log10(stat-P)",
    color = "Organ"
  ) +
  theme_minimal() +  # Apply minimal theme for clarity
  theme(
    panel.border = element_rect(fill=NA,color="black", size=1, linetype="solid"),
    text = element_text(size = 12),  # Adjust text size for readability
    strip.text = element_text(color = "black", size = 12, face = "bold"),  # Customize facet labels
    axis.text.x = element_text(angle = 90, hjust = 1)  # Rotate x-axis labels for better visibility
  ) +
  scale_color_brewer(palette = "Set1") + 
   geom_hline(yintercept = -log10(0.05), linetype="dotted",color = "red", size=0.5)



p3

p4=ggplot(scDRS_common %>%
         filter(Strategy == "mBAT-combo window 10kb") %>%
         filter(!Property == "Resultant"),
       aes(x = log10(n_cell), y = -log10(assoc_mcp), color = organ)) +
  geom_point(size = 1.5, alpha = 0.7) +  # Add points to represent P values
  geom_abline(intercept = 0, slope = 1, linetype = "dashed", color = "grey") +  # Add 45-degree line
  geom_smooth(method = "lm", se = FALSE, linetype = "solid", color = "black") +  # Add linear correlation line
  facet_wrap(~ Property, scales = "free_x") +  # Facet by Property
  labs(
    x = "log10(Cell number within Cell type)",
    y = "log10(MC-P)",
    color = "Organ"
  ) +
  theme_minimal() +  # Apply minimal theme for clarity
  theme(
    panel.border = element_rect(fill=NA,color="black", size=1, linetype="solid"),
    text = element_text(size = 12),  # Adjust text size for readability
    strip.text = element_text(color = "black", size = 12, face = "bold"),  # Customize facet labels
    axis.text.x = element_text(angle = 90, hjust = 1)  # Rotate x-axis labels for better visibility
  ) +
  scale_color_brewer(palette = "Set1") + 
   geom_hline(yintercept = -log10(0.05), linetype="dotted",color = "red", size=0.5)



p4

```






















