
scp -r ~/Manuscript_Ang/Benchmark_comparison/Code/Code_final/One_side_MG_con_scripts_improve uqali4@bunya.rcc.uq.edu.au:/scratch/user/uqali4/

scp -r uqali4@bunya.rcc.uq.edu.au:/scratch/user/uqali4/geneset_res/cepo_s_MAGMAgeneset_continuous_oneside_results.txt ~/Manuscript_Ang/Benchmark_comparison/

scp -r uqali4@bunya.rcc.uq.edu.au:/scratch/user/uqali4/geneset_res/sclinker_s_MAGMAgeneset_continuous_oneside_results.txt ~/Manuscript_Ang/Benchmark_comparison/



# Step1: Convert the format of annotation for CELLEX to MAGMA-geneset
```{r}

library(data.table)

# Define the directories and lists
dir <- "/scratch/user/uqali4/Cepo_esw/"
metrics_dirs <- c("Cepo_s")
prefix_list <- c(
  "2019_Smillie_normal_cellxgene",
  "2019_Smillie_normal_cellxgene_pc",
  "Cheng_2018_Cell_Reports_updated",
  "Cheng_2018_Cell_Reports_pc",
  "FBM_Jardine_2021_Nature",
  "FBM_Jardine_2021_Nature_pc",
  "human_liver_atlas_Guilliams_2022_cell",
  "human_liver_atlas_Guilliams_2022_cell_pc",
  "TMS_pc_ortholog_with_TS_minCell20",
  "TabulaSapiens_pc_ortholog_with_TMS_minCell20",
  "Fasolino_2022_Nat_Metab_normal_only",
  "Fasolino_2022_Nat_Metab_normal_only_pc",
  "CARE_snRNA_Heart_expr_gene_withPos",
  "CARE_snRNA_Heart_pc",
  "HLCA_core_healthy_LP_expr_gene_withPos",
  "HLCA_core_healthy_LP_pc",
  "Kamath_2022_normal_expr_gene_withPos",
  "Kamath_2022_normal_pc"
)



# Loop through each prefix and metric
for (prefix in prefix_list) {
  for (metrics in metrics_dirs) {
    
    # Construct the file path for reading
    input_file <- paste0(dir,"cepo_norm_", prefix,".", metrics, ".csv")
    
    # Read the CSV file
    df <- fread(input_file)
    
    # Construct the output file path
    output_file <- paste0("/scratch/project/genetic_data_analysis/uqali4/MG_set_conAnnot/", prefix, ".", metrics, ".csv")
    
    # Write the data frame to the new file
    write.table(df, output_file, sep = "\t", row.names = FALSE, quote = FALSE)
   
  }
}

#########################################################################################################################################################

#########################################################################################################################################################
library(data.table)

dir <- "/scratch/user/uqali4/sclinker_esw/"
metrics_dirs <- c("sclinker_s")
prefix_list <- c(
  "2019_Smillie_normal_cellxgene",
  "2019_Smillie_normal_cellxgene_pc",
  "Cheng_2018_Cell_Reports_updated",
  "Cheng_2018_Cell_Reports_pc",
  "FBM_Jardine_2021_Nature",
  "FBM_Jardine_2021_Nature_pc",
  "human_liver_atlas_Guilliams_2022_cell",
  "human_liver_atlas_Guilliams_2022_cell_pc",
  "tms_facs_1to1",
  "ts_pc_1to1",
  "Fasolino_2022_Nat_Metab_normal_only",
  "Fasolino_2022_Nat_Metab_normal_only_pc",
  "CARE_all_genes",
  "CARE_pc_only",
  "HCLA_LP_allgenes",  
  "HCLA_LP_pc",
  "Kamath_allgenes",
  "Kamath_pc_only"
)



# Loop through each prefix and metric
for (prefix in prefix_list) {
  for (metrics in metrics_dirs) {
    
    # Construct the file path for reading
    input_file <- paste0(dir,prefix,".", metrics, ".csv")
    
    # Read the CSV file
    df <- fread(input_file)
    
    # Construct the output file path
    output_file <- paste0("/scratch/project/genetic_data_analysis/uqali4/MG_set_conAnnot/", prefix, ".", metrics, ".csv")
    
    # Write the data frame to the new file
    write.table(df, output_file, sep = "\t", row.names = FALSE, quote = FALSE)
   
  }
}

```

# Step2: Generate a list of files for all genes organ with one side for Cepo_s

```{r}

# Define prefixes
prefix_list <- c("2019_Smillie_normal_cellxgene",
                 "CARE_snRNA_Heart_expr_gene_withPos",
                 "Cheng_2018_Cell_Reports_updated", 
                 "Fasolino_2022_Nat_Metab_normal_only",
                 "HLCA_core_healthy_LP_expr_gene_withPos",
                 "FBM_Jardine_2021_Nature",
                 "human_liver_atlas_Guilliams_2022_cell",
                 "Kamath_2022_normal_expr_gene_withPos")

# Define metrics
metrics_dirs <- c("Cepo_s")

# Directory for generated scripts
output_dir <- "~/Manuscript_Ang/Benchmark_comparison/Code/Code_final/One_side_MG_con_scripts_improve/"

# Template for bash script
template <- "#!/bin/bash
#SBATCH --nodes=1
#SBATCH --ntasks-per-node=1
#SBATCH --cpus-per-task=8
#SBATCH --mem=10G
#SBATCH --time=12:00:00
#SBATCH --job-name=%s_cepo_s_magma_geneset_benchmark_100kb
#SBATCH --error=slurm_%%A_%%a.error
#SBATCH --output=slurm_%%A_%%a.out
#SBATCH --partition=general
#SBATCH --account=a_mcrae
#SBATCH --array=1-39

i=$SLURM_ARRAY_TASK_ID

TASKFILE=\"/QRISdata/Q5729/job_list.txt\"
trait=$(sed -n \"${i}p\" $TASKFILE)
trait=$(echo \"$trait\" | sed 's/^[[:space:]]*//;s/[[:space:]]*$//')

echo \"Trimmed Trait: '$trait'\"
echo ${i}
trait_magma_dir=\"/scratch/project/genetic_data_analysis/uqali4/MAGMA_10kb_UKB20k_56778genes\"
metrics_dirs=(%s) 
for dir_name in \"${metrics_dirs[@]}\"; do
  COVAR_FILE=\"/scratch/project/genetic_data_analysis/uqali4/MG_set_conAnnot/%s.${dir_name}.csv\"
  mkdir -p /scratch/user/uqali4/geneset_res/Con_MG_set_oneside/%s/${dir_name}
  new_res_dir=\"/scratch/user/uqali4/geneset_res/Con_MG_set_oneside/%s/${dir_name}\"
  /scratch/project/genetic_data_analysis/uqali4/software/magma --gene-results $trait_magma_dir/magma.${trait}.genes.raw --gene-covar $COVAR_FILE --model direction=pos --out $new_res_dir/${trait}
done
"

# Function to generate bash script for each prefix
generate_script <- function(prefix, metrics_dirs, output_dir) {
  # Format the metrics_dirs array for bash
  metrics_str <- paste(metrics_dirs, collapse=" ")
  
  # Generate the script content by replacing the placeholders
  script_content <- sprintf(template, prefix, metrics_str, prefix, prefix, prefix)
  
  # Define the output file name
  script_file <- file.path(output_dir, paste0(prefix, "_cepo_s_magma_geneset_benchmark.sh"))
  
  # Write the script to a file
  writeLines(script_content, script_file)
  
  # Output message to indicate the file is written
  cat("Generated script for:", prefix, "\n")
}

# Generate the scripts for each prefix
for (prefix in prefix_list) {
  generate_script(prefix, metrics_dirs, output_dir)
}

```

# Step2: Generate a list of files for all genes organ with one side for sclinker_s

```{r}

# Define prefixes
prefix_list <- c("2019_Smillie_normal_cellxgene",
                 "CARE_all_genes",
                 "Cheng_2018_Cell_Reports_updated", 
                 "Fasolino_2022_Nat_Metab_normal_only",
                 "HCLA_LP_allgenes",
                 "FBM_Jardine_2021_Nature",
                 "human_liver_atlas_Guilliams_2022_cell",
                 "Kamath_allgenes")

# Define metrics
metrics_dirs <- c("sclinker_s")

# Directory for generated scripts
output_dir <- "~/Manuscript_Ang/Benchmark_comparison/Code/Code_final/One_side_MG_con_scripts_improve/"

# Template for bash script
template <- "#!/bin/bash
#SBATCH --nodes=1
#SBATCH --ntasks-per-node=1
#SBATCH --cpus-per-task=8
#SBATCH --mem=10G
#SBATCH --time=12:00:00
#SBATCH --job-name=%s_sclinker_s_magma_geneset_benchmark_100kb
#SBATCH --error=slurm_%%A_%%a.error
#SBATCH --output=slurm_%%A_%%a.out
#SBATCH --partition=general
#SBATCH --account=a_mcrae
#SBATCH --array=1-39

i=$SLURM_ARRAY_TASK_ID

TASKFILE=\"/QRISdata/Q5729/job_list.txt\"
trait=$(sed -n \"${i}p\" $TASKFILE)
trait=$(echo \"$trait\" | sed 's/^[[:space:]]*//;s/[[:space:]]*$//')

echo \"Trimmed Trait: '$trait'\"
echo ${i}
trait_magma_dir=\"/scratch/project/genetic_data_analysis/uqali4/MAGMA_10kb_UKB20k_56778genes\"
metrics_dirs=(%s) 
for dir_name in \"${metrics_dirs[@]}\"; do
  COVAR_FILE=\"/scratch/project/genetic_data_analysis/uqali4/MG_set_conAnnot/%s.${dir_name}.csv\"
  mkdir -p /scratch/user/uqali4/geneset_res/Con_MG_set_oneside/%s/${dir_name}
  new_res_dir=\"/scratch/user/uqali4/geneset_res/Con_MG_set_oneside/%s/${dir_name}\"
  /scratch/project/genetic_data_analysis/uqali4/software/magma --gene-results $trait_magma_dir/magma.${trait}.genes.raw --gene-covar $COVAR_FILE --model direction=pos --out $new_res_dir/${trait}
done
"

# Function to generate bash script for each prefix
generate_script <- function(prefix, metrics_dirs, output_dir) {
  # Format the metrics_dirs array for bash
  metrics_str <- paste(metrics_dirs, collapse=" ")
  
  # Generate the script content by replacing the placeholders
  script_content <- sprintf(template, prefix, metrics_str, prefix, prefix, prefix)
  
  # Define the output file name
  script_file <- file.path(output_dir, paste0(prefix, "_sclinker_s_magma_geneset_benchmark.sh"))
  
  # Write the script to a file
  writeLines(script_content, script_file)
  
  # Output message to indicate the file is written
  cat("Generated script for:", prefix, "\n")
}

# Generate the scripts for each prefix
for (prefix in prefix_list) {
  generate_script(prefix, metrics_dirs, output_dir)
}

```

# Step2: Generate a list of files for PC organn for Cepo_s with one side 
```{r}
# Define prefixes
prefix_list <- c("HLCA_core_healthy_LP_pc",
                 "2019_Smillie_normal_cellxgene_pc",
                 "CARE_snRNA_Heart_pc",
                 "Cheng_2018_Cell_Reports_pc", 
                 "Fasolino_2022_Nat_Metab_normal_only_pc",
                 "FBM_Jardine_2021_Nature_pc",
                 "human_liver_atlas_Guilliams_2022_cell_pc",
                 "Kamath_2022_normal_pc")

# Define metrics
metrics_dirs <- c("Cepo_s")

# Directory for generated scripts
output_dir <- "~/Manuscript_Ang/Benchmark_comparison/Code/Code_final/One_side_MG_con_scripts_improve/"

# Template for bash script
template <- "#!/bin/bash
#SBATCH --nodes=1
#SBATCH --ntasks-per-node=1
#SBATCH --cpus-per-task=8
#SBATCH --mem=10G
#SBATCH --time=12:00:00
#SBATCH --job-name=%s_cepo_s_magma_geneset_benchmark_100kb
#SBATCH --error=slurm_%%A_%%a.error
#SBATCH --output=slurm_%%A_%%a.out
#SBATCH --partition=general
#SBATCH --account=a_mcrae
#SBATCH --array=1-39

i=$SLURM_ARRAY_TASK_ID

TASKFILE=\"/QRISdata/Q5729/job_list.txt\"
trait=$(sed -n \"${i}p\" $TASKFILE)
trait=$(echo \"$trait\" | sed 's/^[[:space:]]*//;s/[[:space:]]*$//')

echo \"Trimmed Trait: '$trait'\"
echo ${i}
trait_magma_dir=\"/scratch/project/genetic_data_analysis/uqali4/MAGMA_10kb_UKB20k_56778genes_pc\"
metrics_dirs=(%s) 
for dir_name in \"${metrics_dirs[@]}\"; do
  COVAR_FILE=\"/scratch/project/genetic_data_analysis/uqali4/MG_set_conAnnot/%s.${dir_name}.csv\"
  mkdir -p /scratch/user/uqali4/geneset_res/Con_MG_set_oneside/%s/${dir_name}
  new_res_dir=\"/scratch/user/uqali4/geneset_res/Con_MG_set_oneside/%s/${dir_name}\"
  /scratch/project/genetic_data_analysis/uqali4/software/magma --gene-results $trait_magma_dir/magma.${trait}.genes.raw --gene-covar $COVAR_FILE --model direction=pos --out $new_res_dir/${trait}
done
"

# Function to generate bash script for each prefix
generate_script <- function(prefix, metrics_dirs, output_dir) {
  # Format the metrics_dirs array for bash
  metrics_str <- paste(metrics_dirs, collapse=" ")
  
  # Generate the script content by replacing the placeholders
  script_content <- sprintf(template, prefix, metrics_str, prefix, prefix, prefix)
  
  # Define the output file name
  script_file <- file.path(output_dir, paste0(prefix, "_cepo_s_magma_geneset_benchmark.sh"))
  
  # Write the script to a file
  writeLines(script_content, script_file)
  
  # Output message to indicate the file is written
  cat("Generated script for:", prefix, "\n")
}

# Generate the scripts for each prefix
for (prefix in prefix_list) {
  generate_script(prefix, metrics_dirs, output_dir)
}

```

# Step2: Generate a list of files for PC organn for sclinker_s with one side 
```{r}
# Define prefixes
prefix_list <- c("HLCA_core_healthy_LP_pc",
                 "2019_Smillie_normal_cellxgene_pc",
                 "CARE_pc_only",
                 "Cheng_2018_Cell_Reports_pc", 
                 "Fasolino_2022_Nat_Metab_normal_only_pc",
                 "FBM_Jardine_2021_Nature_pc",
                 "human_liver_atlas_Guilliams_2022_cell_pc",
                 "Kamath_pc_only")

# Define metrics
metrics_dirs <- c("sclinker_s")

# Directory for generated scripts
output_dir <- "~/Manuscript_Ang/Benchmark_comparison/Code/Code_final/One_side_MG_con_scripts_improve/"

# Template for bash script
template <- "#!/bin/bash
#SBATCH --nodes=1
#SBATCH --ntasks-per-node=1
#SBATCH --cpus-per-task=8
#SBATCH --mem=10G
#SBATCH --time=12:00:00
#SBATCH --job-name=%s_sclinker_s_magma_geneset_benchmark_100kb
#SBATCH --error=slurm_%%A_%%a.error
#SBATCH --output=slurm_%%A_%%a.out
#SBATCH --partition=general
#SBATCH --account=a_mcrae
#SBATCH --array=1-39

i=$SLURM_ARRAY_TASK_ID

TASKFILE=\"/QRISdata/Q5729/job_list.txt\"
trait=$(sed -n \"${i}p\" $TASKFILE)
trait=$(echo \"$trait\" | sed 's/^[[:space:]]*//;s/[[:space:]]*$//')

echo \"Trimmed Trait: '$trait'\"
echo ${i}
trait_magma_dir=\"/scratch/project/genetic_data_analysis/uqali4/MAGMA_10kb_UKB20k_56778genes_pc\"
metrics_dirs=(%s) 
for dir_name in \"${metrics_dirs[@]}\"; do
  COVAR_FILE=\"/scratch/project/genetic_data_analysis/uqali4/MG_set_conAnnot/%s.${dir_name}.csv\"
  mkdir -p /scratch/user/uqali4/geneset_res/Con_MG_set_oneside/%s/${dir_name}
  new_res_dir=\"/scratch/user/uqali4/geneset_res/Con_MG_set_oneside/%s/${dir_name}\"
  /scratch/project/genetic_data_analysis/uqali4/software/magma --gene-results $trait_magma_dir/magma.${trait}.genes.raw --gene-covar $COVAR_FILE --model direction=pos --out $new_res_dir/${trait}
done
"

# Function to generate bash script for each prefix
generate_script <- function(prefix, metrics_dirs, output_dir) {
  # Format the metrics_dirs array for bash
  metrics_str <- paste(metrics_dirs, collapse=" ")
  
  # Generate the script content by replacing the placeholders
  script_content <- sprintf(template, prefix, metrics_str, prefix, prefix, prefix)
  
  # Define the output file name
  script_file <- file.path(output_dir, paste0(prefix, "_sclinker_s_magma_geneset_benchmark.sh"))
  
  # Write the script to a file
  writeLines(script_content, script_file)
  
  # Output message to indicate the file is written
  cat("Generated script for:", prefix, "\n")
}

# Generate the scripts for each prefix
for (prefix in prefix_list) {
  generate_script(prefix, metrics_dirs, output_dir)
}

```

# Generate for TMS and TS

# Step2: TMS for one side
```{bash}
#!/bin/bash
#SBATCH --nodes=1
#SBATCH --ntasks-per-node=1
#SBATCH --cpus-per-task=8
#SBATCH --mem=10G
#SBATCH --time=12:00:00
#SBATCH --job-name=tms_pc_mg
#SBATCH --error=slurm_%A_%a.error
#SBATCH --output=slurm_%A_%a.out
#SBATCH --partition=general
#SBATCH --account=a_mcrae
#SBATCH --array=1-39

i=$SLURM_ARRAY_TASK_ID

TASKFILE="/QRISdata/Q5729/job_list.txt"
trait=$(sed -n "${i}p" $TASKFILE)
trait=$(echo "$trait" | sed 's/^[[:space:]]*//;s/[[:space:]]*$//')

echo "Trimmed Trait: '$trait'"
echo ${i}
trait_magma_dir="/scratch/project/genetic_data_analysis/uqali4/MAGMA_10kb_UKB20k_56778genes_pc_tms_ts_consist"
metrics_dirs=("Cepo_s" "sclinker_s") 
for dir_name in "${metrics_dirs[@]}"; do
  COVAR_FILE="/scratch/project/genetic_data_analysis/uqali4/MG_set_conAnnot/tms_facs_1to1.${dir_name}.csv"
  mkdir -p /scratch/user/uqali4/geneset_res/Con_MG_set_oneside/tms_pc/${dir_name}
  new_res_dir="/scratch/user/uqali4/geneset_res/Con_MG_set_oneside/tms_pc/${dir_name}"
  /scratch/project/genetic_data_analysis/uqali4/software/magma --gene-results $trait_magma_dir/magma.${trait}.genes.raw --gene-covar $COVAR_FILE --model direction=pos --out $new_res_dir/${trait}
done


```

# Step2: TS for one side
```{bash}
#!/bin/bash
#SBATCH --nodes=1
#SBATCH --ntasks-per-node=1
#SBATCH --cpus-per-task=8
#SBATCH --mem=10G
#SBATCH --time=12:00:00
#SBATCH --job-name=ts_pc_mg
#SBATCH --error=slurm_%A_%a.error
#SBATCH --output=slurm_%A_%a.out
#SBATCH --partition=general
#SBATCH --account=a_mcrae
#SBATCH --array=1-39

i=$SLURM_ARRAY_TASK_ID

TASKFILE="/QRISdata/Q5729/job_list.txt"
trait=$(sed -n "${i}p" $TASKFILE)
trait=$(echo "$trait" | sed 's/^[[:space:]]*//;s/[[:space:]]*$//')

echo "Trimmed Trait: '$trait'"
echo ${i}
trait_magma_dir="/scratch/project/genetic_data_analysis/uqali4/MAGMA_10kb_UKB20k_56778genes_pc_tms_ts_consist"
metrics_dirs=("Cepo_s" "sclinker_s"") 
for dir_name in "${metrics_dirs[@]}"; do
  COVAR_FILE="/scratch/project/genetic_data_analysis/uqali4/MG_set_conAnnot/ts_pc_1to1.${dir_name}.csv"
  mkdir -p /scratch/user/uqali4/geneset_res/Con_MG_set_oneside/ts_pc/${dir_name}
  new_res_dir="/scratch/user/uqali4/geneset_res/Con_MG_set_oneside/ts_pc/${dir_name}"
  /scratch/project/genetic_data_analysis/uqali4/software/magma --gene-results $trait_magma_dir/magma.${trait}.genes.raw --gene-covar $COVAR_FILE --model direction=pos --out $new_res_dir/${trait}
done


```

# Submit all scripts
cd /scratch/project/genetic_data_analysis/uqali4/tmp 
rm *
```{bash}
#!/bin/bash

# Define the directory containing the generated scripts
script_dir="/scratch/user/uqali4/One_side_MG_con_scripts_improve"

# Loop through each bash script in the directory and submit it
cd /scratch/project/genetic_data_analysis/uqali4/tmp 
for script in "$script_dir"/*.sh; do
    if [[ -f "$script" ]]; then
        echo "Submitting $script"
        sbatch "$script"
    else
        echo "No bash scripts found in $script_dir"
    fi
done


```


# Collect results of Con_MG_set_oneside for Cepo_s
```{r}
library(tidyverse)
library(data.table)

# Define the CT directories directly (no more file prefixes)
ct_directories <- c(
  "2019_Smillie_normal_cellxgene",
  "2019_Smillie_normal_cellxgene_pc",
  "Cheng_2018_Cell_Reports_updated",
  "Cheng_2018_Cell_Reports_pc",
  "FBM_Jardine_2021_Nature",
  "FBM_Jardine_2021_Nature_pc",
  "human_liver_atlas_Guilliams_2022_cell",
  "human_liver_atlas_Guilliams_2022_cell_pc",
  "ts_pc",
  "tms_pc",
  "Fasolino_2022_Nat_Metab_normal_only",
  "Fasolino_2022_Nat_Metab_normal_only_pc",
  "CARE_snRNA_Heart_expr_gene_withPos",
  "CARE_snRNA_Heart_pc",
  "HLCA_core_healthy_LP_expr_gene_withPos",
  "HLCA_core_healthy_LP_pc",
  "Kamath_2022_normal_expr_gene_withPos",
  "Kamath_2022_normal_pc"
)

# Define the metrics directories
metrics_dirs <- c("Cepo_s")

# Define traits
traits_dt <- fread("/QRISdata/Q5729/job_list.txt", h = FALSE)
names(traits_dt) <- "file"
traits <- traits_dt$file

# Define the base directory
base_dir <- "/scratch/user/uqali4/geneset_res/Con_MG_set_oneside"

# Initialize an empty data frame to store all results
all <- NULL

# Loop over each CT directory, metric directory, and trait
for (ct_dir in ct_directories) {
  for (dir_name in metrics_dirs) {
    for (trait in traits) {
      
      # Construct the file path based on the CT directory, metric, and trait
      file_path <- paste0(base_dir, "/", ct_dir, "/", dir_name, "/", trait, ".gsa.out")
      
      # Check if the file exists
      if (file.exists(file_path)) {
        # Read the file if it exists
        df <- read.table(file_path, skip = 3, header = TRUE)
        
        # Check if the column 'FULL_NAME' exists, if not add it
        if (!"FULL_NAME" %in% colnames(df)) {
          df$FULL_NAME <- df$VARIABLE
        }
        
        # Add additional columns
        df$Dataset <- ct_dir
        df$Trait <- trait
        df$Metrics <- dir_name
        df$Method <- "MAGMA set continuous one side"
        
        # Reorder columns as specified
        df <- df[, c("VARIABLE", "TYPE", "NGENES", "BETA", "BETA_STD", "SE", "P",
                     "FULL_NAME", "Dataset", "Trait", "Metrics", "Method")]
        
        # Combine with the 'all' dataframe
        all <- rbind(all, df)
      } else {
        # Optionally print a message if the file does not exist
        cat("File does not exist:", file_path, "\n")
      }
    }
  }
}

# Select relevant columns and write to the output file
op <- all %>% select(!c("VARIABLE", "TYPE"))

# Write the result to a file
write.table(op, "/scratch/user/uqali4/geneset_res/cepo_s_MAGMAgeneset_continuous_oneside_results.txt",
            row.names = FALSE, col.names = TRUE, quote = FALSE, sep = "\t")

```


# Collect results of Con_MG_set_oneside for sclinker_s
```{r}
library(tidyverse)
library(data.table)

# Define the CT directories directly (no more file prefixes)
ct_directories <- c(
 "2019_Smillie_normal_cellxgene",
                 "CARE_all_genes",
                 "Cheng_2018_Cell_Reports_updated", 
                 "Fasolino_2022_Nat_Metab_normal_only",
                 "HCLA_LP_allgenes",
                 "FBM_Jardine_2021_Nature",
                 "human_liver_atlas_Guilliams_2022_cell",
                 "Kamath_allgenes",
  "ts_pc",
  "tms_pc",
 "HLCA_core_healthy_LP_pc",
                 "2019_Smillie_normal_cellxgene_pc",
                 "CARE_pc_only",
                 "Cheng_2018_Cell_Reports_pc", 
                 "Fasolino_2022_Nat_Metab_normal_only_pc",
                 "FBM_Jardine_2021_Nature_pc",
                 "human_liver_atlas_Guilliams_2022_cell_pc",
                 "Kamath_pc_only")


# Define the metrics directories
metrics_dirs <- c("sclinker_s")

# Define traits
traits_dt <- fread("/QRISdata/Q5729/job_list.txt", h = FALSE)
names(traits_dt) <- "file"
traits <- traits_dt$file

# Define the base directory
base_dir <- "/scratch/user/uqali4/geneset_res/Con_MG_set_oneside"

# Initialize an empty data frame to store all results
all <- NULL

# Loop over each CT directory, metric directory, and trait
for (ct_dir in ct_directories) {
  for (dir_name in metrics_dirs) {
    for (trait in traits) {
      
      # Construct the file path based on the CT directory, metric, and trait
      file_path <- paste0(base_dir, "/", ct_dir, "/", dir_name, "/", trait, ".gsa.out")
      
      # Check if the file exists
      if (file.exists(file_path)) {
        # Read the file if it exists
        df <- read.table(file_path, skip = 3, header = TRUE)
        
        # Check if the column 'FULL_NAME' exists, if not add it
        if (!"FULL_NAME" %in% colnames(df)) {
          df$FULL_NAME <- df$VARIABLE
        }
        
        # Add additional columns
        df$Dataset <- ct_dir
        df$Trait <- trait
        df$Metrics <- dir_name
        df$Method <- "MAGMA set continuous one side"
        
        # Reorder columns as specified
        df <- df[, c("VARIABLE", "TYPE", "NGENES", "BETA", "BETA_STD", "SE", "P",
                     "FULL_NAME", "Dataset", "Trait", "Metrics", "Method")]
        
        # Combine with the 'all' dataframe
        all <- rbind(all, df)
      } else {
        # Optionally print a message if the file does not exist
        cat("File does not exist:", file_path, "\n")
      }
    }
  }
}

# Select relevant columns and write to the output file
op <- all %>% select(!c("VARIABLE", "TYPE"))

# Write the result to a file
write.table(op, "/scratch/user/uqali4/geneset_res/sclinker_s_MAGMAgeneset_continuous_oneside_results.txt",row.names = FALSE, col.names = TRUE, quote = FALSE, sep = "\t")

```


















































