scp -r uqali4@bunya.rcc.uq.edu.au:/scratch/user/uqali4/geneset_res/PCgenes_background/TMS_TS_PC_allCT_8metrics_MAGMAgeneset.txt /Users/uqali4/Manuscripts/Benchmark/

scp -r uqali4@bunya.rcc.uq.edu.au:/scratch/user/uqali4/geneset_res/PCgenes_background/All_organ_CT_PC_8metrics_MAGMAgeneset_results.txt /Users/uqali4/Manuscripts/Benchmark/


# Pipeline for TS and TMS based MAGMA gene-set based tests:
metrics_dirs=("TDEP" "cepo_norm" "det.esw_s" "ep.esw_s" "esmu" "ges.esw_s" "nsi.esw_s" "sclinker")
Part of the results:/QRISdata/Q3999/tmp/Benchmark_association/geneset_res/PCgenes_background/tms_pc/${dir_name}/MAGMA_100kb_based
Part of the results:/QRISdata/Q3999/tmp/Benchmark_association/geneset_res/PCgenes_background/ts_pc/${dir_name}/MAGMA_100kb_based
Part of the results:/scratch/user/uqali4/geneset_res/PCgenes_background/ts_pc/${dir_name}/MAGMA_100kb_based
Part of the results:/scratch/user/uqali4/geneset_res/PCgenes_background/tms_pc/${dir_name}/MAGMA_100kb_based
```{r}
library(tidyverse)
library(data.table)

# Define file prefixes (datasets) and metrics
file_prefixes <- c("tms_pc", "ts_pc")
metrics_dirs <- c("TDEP", "cepo_norm", "det.esw_s", "ep.esw_s", "esmu", "ges.esw_s", "nsi.esw_s", "sclinker")

# Define traits
traits_dt <- fread("/QRISdata/Q5729/job_list.txt", h = FALSE)
names(traits_dt) <- "file"
traits <- traits_dt$file

# Initialize an empty data frame to store all results
all <- NULL

# Define the base directories
base_dirs <- c(
  "/QRISdata/Q3999/tmp/Benchmark_association/geneset_res/PCgenes_background",
  "/scratch/user/uqali4/geneset_res/PCgenes_background"
)

# Loop over each base directory, dataset (file prefix), metric directory, and trait
for (base_dir in base_dirs) {
  for (dataset in file_prefixes) {
    for (dir_name in metrics_dirs) {
      for (trait in traits) {
        
        # Construct the file path based on the dataset, metric, and trait
        file_path <- paste0(base_dir, "/", dataset, "/", dir_name, "/MAGMA_100kb_based/", trait, ".gsa.out")
        
        # Check if the file exists
        if (file.exists(file_path)) {
          # Read the file if it exists
          df <- read.table(file_path, skip = 3, header = TRUE)
          
          # Check if the column 'FULL_NAME' exists, if not add it
          if (!"FULL_NAME" %in% colnames(df)) {
            df$FULL_NAME <- df$VARIABLE
          }
          
          # Add additional columns
          df$Dataset <- dataset
          df$Trait <- trait
          df$Metrics <- dir_name
          df$Method <- "MAGMA gene-set"
          
          # Reorder columns as specified
          df <- df[, c("VARIABLE", "TYPE", "NGENES", "BETA", "BETA_STD", "SE", "P",
                       "FULL_NAME", "Dataset", "Trait", "Metrics", "Method")]
          
          # Combine with the 'all' dataframe
          all <- rbind(all, df)
        } else {
          # Optionally print a message if the file does not exist
          cat("File does not exist:", file_path, "\n")
        }
      }
    }
  }
}

# Select relevant columns and write to the output file
op <- all %>% select(!c("VARIABLE", "TYPE"))

# Optionally write the result to a file
write.table(op, "/scratch/user/uqali4/geneset_res/PCgenes_background/TMS_TS_PC_allCT_8metrics_MAGMAgeneset.txt",
             row.names = FALSE, col.names = TRUE, quote = FALSE, sep = "\t")

```


# PC genes results of MG-set from atlas
```{r}
library(tidyverse)
library(data.table)

# Define the CT directories directly (no more file prefixes)
ct_directories <- c(
  "ts_pc",
  "tms_pc"
)

# Define the metrics directories
metrics_dirs <- c("TDEP", "cepo_norm", "det.esw_s", "ep.esw_s", "esmu", "ges.esw_s", "nsi.esw_s", "sclinker")

# Define traits
traits_dt <- fread("/QRISdata/Q5729/job_list.txt", h = FALSE)
names(traits_dt) <- "file"
traits <- traits_dt$file

# Initialize an empty data frame to store all results
all <- NULL

# Define the base directory
base_dir <- "/scratch/user/uqali4/geneset_res/PCgenes_background"

# Loop over each CT directory, metric directory, and trait
for (ct_dir in ct_directories) {
  for (dir_name in metrics_dirs) {
    for (trait in traits) {
      
      # Construct the file path based on the CT directory, metric, and trait
      file_path <- paste0(base_dir, "/", ct_dir, "/", dir_name, "/MAGMA_100kb_based/", trait, ".gsa.out")
      
      # Check if the file exists
      if (file.exists(file_path)) {
        # Read the file if it exists
        print(file_path)
        df <- read.table(file_path, skip = 3, header = TRUE)
        
        # Check if the column 'FULL_NAME' exists, if not add it
        if (!"FULL_NAME" %in% colnames(df)) {
          df$FULL_NAME <- df$VARIABLE
        }
        
        # Add additional columns
        df$Dataset <- ct_dir
        df$Trait <- trait
        df$Metrics <- dir_name
        df$Method <- "MAGMA gene-set"
        df$gene_group <- "PCgene"
        
        # Reorder columns as specified
        df <- df[, c("VARIABLE", "TYPE", "NGENES", "BETA", "BETA_STD", "SE", "P",
                     "FULL_NAME", "Dataset", "Trait", "Metrics", "Method","gene_group")]
        
        # Combine with the 'all' dataframe
        all <- rbind(all, df)
      } else {
        # Optionally print a message if the file does not exist
        cat("File does not exist:", file_path, "\n")
      }
    }
  }
}

# Select relevant columns and write to the output file
op <- all %>% select(!c("VARIABLE", "TYPE"))

# Write the result to a file
write.table(op, "/scratch/user/uqali4/geneset_res/PCgenes_background/TMS_TS_PC_allCT_8metrics_MAGMAgeneset.txt",
            row.names = FALSE, col.names = TRUE, quote = FALSE, sep = "\t")

```


# PC genes results of MG-set from single organ
```{r}
library(tidyverse)
library(data.table)

# Define the CT directories directly (no more file prefixes)
ct_directories <- c(
  "ctd_2019_Smillie_normal_cellxgene_pc",
  "ctd_Cheng_2018_Cell_Reports_pc",
  "ctd_Fasolino_2022_Nat_Metab_normal_only_pc",
  "ctd_FBM_Jardine_2021_Nature_pc",
  "ctd_human_liver_atlas_Guilliams_2022_cell_pc",
  "HLCA_core_healthy_pc",
  "Kamath_2022_normal_pc",
  "CARE_pc"
)

# Define the metrics directories
metrics_dirs <- c("TDEP", "cepo_norm", "det.esw_s", "ep.esw_s", "esmu", "ges.esw_s", "nsi.esw_s", "sclinker")

# Define traits
traits_dt <- fread("/QRISdata/Q5729/job_list.txt", h = FALSE)
names(traits_dt) <- "file"
traits <- traits_dt$file

# Initialize an empty data frame to store all results
all <- NULL

# Define the base directory
base_dir <- "/scratch/user/uqali4/geneset_res/PCgenes_background"

# Loop over each CT directory, metric directory, and trait
for (ct_dir in ct_directories) {
  for (dir_name in metrics_dirs) {
    for (trait in traits) {
      
      # Construct the file path based on the CT directory, metric, and trait
      file_path <- paste0(base_dir, "/", ct_dir, "/", dir_name, "/MAGMA_100kb_based/", trait, ".gsa.out")
      
      # Check if the file exists
      if (file.exists(file_path)) {
        # Read the file if it exists
        df <- read.table(file_path, skip = 3, header = TRUE)
        
        # Check if the column 'FULL_NAME' exists, if not add it
        if (!"FULL_NAME" %in% colnames(df)) {
          df$FULL_NAME <- df$VARIABLE
        }
        
        # Add additional columns
        df$Dataset <- ct_dir
        df$Trait <- trait
        df$Metrics <- dir_name
        df$Method <- "MAGMA gene-set"
        df$gene_group <- "PCgene"
        
        # Reorder columns as specified
        df <- df[, c("VARIABLE", "TYPE", "NGENES", "BETA", "BETA_STD", "SE", "P",
                     "FULL_NAME", "Dataset", "Trait", "Metrics", "Method","gene_group")]
        
        # Combine with the 'all' dataframe
        all <- rbind(all, df)
      } else {
        # Optionally print a message if the file does not exist
        cat("File does not exist:", file_path, "\n")
      }
    }
  }
}

# Select relevant columns and write to the output file
op <- all %>% select(!c("VARIABLE", "TYPE"))

# Write the result to a file
write.table(op, "/scratch/user/uqali4/geneset_res/PCgenes_background/All_organ_CT_PC_8metrics_MAGMAgeneset_results.txt",
            row.names = FALSE, col.names = TRUE, quote = FALSE, sep = "\t")

```





# The specificity value is ready;
# The background genes should be the corresponding PC genes instead of all genes' based results.

# Step01: Exact the PC genes results part 
# 01. TMS-TS concordant PC genes
 I reran MAGMA-gene test with different gene annotations agian:~/Manuscript_Ang/Benchmark_comparison/Code/Code_final/MAGMA_gene_based_Test.Rmd
# Output:/scratch/project/genetic_data_analysis/uqali4/MAGMA_10kb_UKB20k_56778genes_pc_tms_ts_consist
gene_pc <- fread("/QRISdata/Q5059/data/ts/TMS_ortholog_with_TS_minCell20_pcgene_list.csv")

# NOT useful below:
```{r}

library(data.table)

# Define file paths
gene_output_dir <- "/scratch/project/genetic_data_analysis/uqali4/MAGMA_10kb_UKB20k_56778genes/"
pcgene_list_file <- "/QRISdata/Q5059/data/ts/TMS_ortholog_with_TS_minCell20_pcgene_list.csv"
output_dir <- "/scratch/project/genetic_data_analysis/uqali4/MAGMA_10kb_UKB20k_56778genes_pc_tms_ts_consist/"

# Create the output directory if it doesn't exist
if (!dir.exists(output_dir)) {
  dir.create(output_dir, recursive = TRUE)
}

# Read the pcgene list
pcgene_list <- fread(pcgene_list_file)$Gene

# Get all *.genes.out files in the directory
gene_files <- list.files(path = gene_output_dir, pattern = "*.genes.out", full.names = TRUE)

# Function to extract matching genes from each file
process_gene_file <- function(file) {
  # Read the gene file
  gene_data <- fread(file)
  
  # Filter for genes in the pcgene list
  filtered_genes <- gene_data[GENE %in% pcgene_list]
  
  # Define the output file name
  output_file <- paste0(output_dir, basename(file))
  
  # Save the filtered data
  fwrite(filtered_genes, output_file)
}

# Apply the function to all gene files
lapply(gene_files, process_gene_file)




```

# 02. Human PC genes
I reran MAGMA-gene test with different gene annotations agian:~/Manuscript_Ang/Benchmark_comparison/Code/Code_final/MAGMA_gene_based_Test.Rmd
# NOT useful below: 
# Output: /scratch/project/genetic_data_analysis/uqali4/MAGMA_10kb_UKB20k_56778genes_pc
```{r}
library(data.table)
library(dplyr)
library(tidyverse)
library(reshape2)

# Define file paths
input_dir <- "/scratch/project/genetic_data_analysis/uqali4/MAGMA_10kb_UKB20k_56778genes/"

# Filter for protein-coding genes if file ends in _pc

# Read gene coordinates file and process
gene_coordinates <- read_tsv("/scratch/project/genetic_data_analysis/uqali4/geneMatrix.56778genes.tsv",
                             col_names = TRUE, col_types = 'cciicc') %>% filter(gene_type == "protein_coding") 

output_dir <- "/scratch/project/genetic_data_analysis/uqali4/MAGMA_10kb_UKB20k_56778genes_pc/"

gene_pc_vec <- gene_coordinates$Gene

# List all .genes.raw files in the input directory
gene_files <- list.files(path = input_dir, pattern = "*.genes.raw", full.names = TRUE)

# Function to filter and save genes from .genes.raw files
filter_and_save_genes <- function(file_path, gene_list, output_dir) {
  # Read the raw file line by line
  lines <- readLines(file_path)
  
  # Separate the header (lines starting with #)
  header <- lines[grepl("^#", lines)]
  
  # Filter the data lines (not starting with #) by gene name
  data_lines <- lines[!grepl("^#", lines)]
  filtered_data_lines <- data_lines[sapply(data_lines, function(line) {
    gene_id <- strsplit(line, " ")[[1]][1]  # Extract the gene ID (first column)
    return(gene_id %in% gene_list)
  })]
  
  # Define output file name
  output_file <- paste0(output_dir, basename(file_path))
  
  # Write the header to the output file
  writeLines(header, con = output_file)
  
  # Append the filtered data to the output file
  cat(filtered_data_lines, sep = "\n", file = output_file, append = TRUE)
  
  # Print a message
  cat("Filtered file saved:", output_file, "\n")
}

# Loop through each .genes.raw file and apply the filtering
for (file in gene_files) {
  filter_and_save_genes(file, gene_pc_vec, output_dir)
}

```


# Step02: Run MAGMA gene-set based tests.

cd /home/uqali4/uqali4/scripts/MGset/PC

vi 2019_Smillie_normal_cellxgene_pc_magma_geneset_benchmark_100kb.sh
```{bash}
#!/bin/bash
#SBATCH --nodes=1
#SBATCH --ntasks-per-node=1
#SBATCH --cpus-per-task=8
#SBATCH --mem=10G
#SBATCH --time=48:00:00
#SBATCH --job-name=ctd_2019_Smillie_normal_cellxgene_pc_magma_geneset_benchmark_100kb
#SBATCH --error=slurm_%A_%a.error
#SBATCH --output=slurm_%A_%a.out
#SBATCH --partition=general
#SBATCH --account=a_mcrae
#SBATCH --array=1-39

i=$SLURM_ARRAY_TASK_ID

TASKFILE="/QRISdata/Q5729/job_list.txt"
trait=$(sed -n "${i}p" $TASKFILE)
trait=$(echo "$trait" | sed 's/^[[:space:]]*//;s/[[:space:]]*$//')

echo "Trimmed Trait: '$trait'"
echo ${i}
trait_magma_dir="/scratch/project/genetic_data_analysis/uqali4/MAGMA_10kb_UKB20k_56778genes_pc"
metrics_dirs=("TDEP" "cepo_norm" "det.esw_s" "ep.esw_s" "esmu" "ges.esw_s" "nsi.esw_s" "sclinker") #"TDEP" "cepo_norm" "det.esw_s" "ep.esw_s" "esmu" 
for dir_name in "${metrics_dirs[@]}"; do
  cell_type="/QRISdata/Q2120/biLDSC/${dir_name}/processed/ctd_2019_Smillie_normal_cellxgene_pc/MAGMA/top10.txt"
  # Check if the output file already exists
  output_file="${res_dir}/${trait}.gsa.out"
  if [ ! -f "$output_file" ]; then
    echo "Running MAGMA for $trait in $dir_name..."
  mkdir -p /scratch/user/uqali4/geneset_res/PCgenes_background/ctd_2019_Smillie_normal_cellxgene_pc/${dir_name}/MAGMA_100kb_based
  new_res_dir="/scratch/user/uqali4/geneset_res/PCgenes_background/ctd_2019_Smillie_normal_cellxgene_pc/${dir_name}/MAGMA_100kb_based"
  /scratch/project/genetic_data_analysis/uqali4/software/magma --gene-results $trait_magma_dir/magma.${trait}.genes.raw --set-annot $cell_type --out $new_res_dir/${trait}
  else
    echo "Output file $output_file already exists. Skipping..."
  fi
done


```



# Bash Script to generated .sh Files
```{bash}
#!/bin/bash
cd /home/uqali4/uqali4/scripts/MGset/PC2
# Define the file prefixes
file_prefixes=(
  "Cheng_2018_Cell_Reports_pc"
  "Fasolino_2022_Nat_Metab_normal_only_pc"
  "FBM_Jardine_2021_Nature_pc"
  "human_liver_atlas_Guilliams_2022_cell_pc"
)

# Read the original script content
original_script="/home/uqali4/scripts/2019_Smillie_normal_cellxgene_pc_magma_geneset_benchmark_100kb.sh"
script_content=$(<"$original_script")

# Loop through each prefix and create a new script with the appropriate prefix
for prefix in "${file_prefixes[@]}"; do
  # Create a new file name based on the prefix
  new_script="${prefix}_magma_geneset_benchmark_100kb.sh"
  
  # Replace the original prefix with the new prefix in the content
  new_content="${script_content//2019_Smillie_normal_cellxgene_pc/$prefix}"
  
  # Write the modified content to the new file
  echo "$new_content" > "$new_script"
  
  echo "Generated script: $new_script"
done

```

vi tms_pc_magma_geneset_benchmark_100kb.sh
```{bash}
#!/bin/bash
#SBATCH --nodes=1
#SBATCH --ntasks-per-node=1
#SBATCH --cpus-per-task=18
#SBATCH --mem=10G
#SBATCH --time=48:00:00
#SBATCH --job-name=tms_pc_magma_geneset_benchmark_100kb
#SBATCH --error=/home/uqali4/jobs_sterr_stout/MAGMA_benchmark/slurm_%A_%a.error
#SBATCH --output=/home/uqali4/jobs_sterr_stout/MAGMA_benchmark/slurm_%A_%a.out
#SBATCH --partition=general
#SBATCH --account=a_mcrae
#SBATCH --array=1-39

i=$SLURM_ARRAY_TASK_ID

TASKFILE="/QRISdata/Q5729/job_list.txt"
trait=$(sed -n "${i}p" $TASKFILE)
trait=$(echo "$trait" | sed 's/^[[:space:]]*//;s/[[:space:]]*$//')

echo "Trimmed Trait: '$trait'"
echo ${i}
trait_magma_dir="/scratch/project/genetic_data_analysis/uqali4/MAGMA_10kb_UKB20k_56778genes_pc_tms_ts_consist"
metrics_dirs=("cepo_norm" "det.esw_s" "TDEP" "esmu" "ges.esw_s" "nsi.esw_s" "sclinker" "ep.esw_s")
for dir_name in "${metrics_dirs[@]}"; do
  cell_type="/QRISdata/Q5514/MGset_full/tms_pc/${dir_name}/MAGMA/top10.txt"
  mkdir -p /QRISdata/Q3999/tmp/Benchmark_association/geneset_res/PCgenes_background/tms_pc/${dir_name}/MAGMA_100kb_based
  res_dir="/QRISdata/Q3999/tmp/Benchmark_association/geneset_res/PCgenes_background/tms_pc/${dir_name}/MAGMA_100kb_based"
  /scratch/project/genetic_data_analysis/uqali4/software/magma --gene-results $trait_magma_dir/magma.${trait}.genes.raw --set-annot $cell_type --out $res_dir/${trait}
done

```

# Bash Script to generated .sh Files
```{bash}
#!/bin/bash
cd /home/uqali4/uqali4/scripts/MGset/PC
# Define the file prefixes
file_prefixes=(
  "tms_pc"
  "ts_pc"
)

# Read the original script content
original_script="tms_pc_magma_geneset_benchmark_100kb.sh"
script_content=$(<"$original_script")

# Loop through each prefix and create a new script with the appropriate prefix
for prefix in "${file_prefixes[@]}"; do
  # Create a new file name based on the prefix
  new_script="${prefix}_magma_geneset_benchmark_100kb.sh"
  
  # Replace the original prefix with the new prefix in the content
  new_content="${script_content//tms_pc/$prefix}"
  
  # Write the modified content to the new file
  echo "$new_content" > "$new_script"
  
  echo "Generated script: $new_script"
done

```

cd /home/uqali4/uqali4/scripts/MGset/PC
vi Kamath_2022_normal_pc_magma_geneset_benchmark_100kb.sh
```{bash}
#!/bin/bash
#SBATCH --nodes=1
#SBATCH --ntasks-per-node=1
#SBATCH --cpus-per-task=18
#SBATCH --mem=10G
#SBATCH --time=48:00:00
#SBATCH --job-name=Kamath_2022_normal_pc_magma_geneset_benchmark_100kb
#SBATCH --error=/home/uqali4/jobs_sterr_stout/MAGMA_benchmark/slurm_%A_%a.error
#SBATCH --output=/home/uqali4/jobs_sterr_stout/MAGMA_benchmark/slurm_%A_%a.out
#SBATCH --partition=general
#SBATCH --account=a_mcrae
#SBATCH --array=1-39

i=$SLURM_ARRAY_TASK_ID

TASKFILE="/QRISdata/Q5729/job_list.txt"
trait=$(sed -n "${i}p" $TASKFILE)
trait=$(echo "$trait" | sed 's/^[[:space:]]*//;s/[[:space:]]*$//')

echo "Trimmed Trait: '$trait'"
echo ${i}
trait_magma_dir="/scratch/project/genetic_data_analysis/uqali4/MAGMA_10kb_UKB20k_56778genes_pc"
metrics_dirs=("cepo_norm" "det.esw_s" "TDEP" "esmu" "ges.esw_s" "nsi.esw_s" "sclinker" "ep.esw_s")
for dir_name in "${metrics_dirs[@]}"; do
  cell_type="/QRISdata/Q5514/Binary_baseline1.1/Kamath_2022_normal_pc/${dir_name}/MAGMA/top10.txt"
  mkdir -p /scratch/user/uqali4/geneset_res/PCgenes_background/Kamath_2022_normal_pc/${dir_name}/MAGMA_100kb_based
  res_dir="/scratch/user/uqali4/geneset_res/PCgenes_background/Kamath_2022_normal_pc/${dir_name}/MAGMA_100kb_based"
  /scratch/project/genetic_data_analysis/uqali4/software/magma --gene-results $trait_magma_dir/magma.${trait}.genes.raw --set-annot $cell_type --out $res_dir/${trait}
done


```


```{bash}
#!/bin/bash
#SBATCH --nodes=1
#SBATCH --ntasks-per-node=1
#SBATCH --cpus-per-task=18
#SBATCH --mem=10G
#SBATCH --time=48:00:00
#SBATCH --job-name=CARE_pc_magma_geneset_benchmark_100kb
#SBATCH --error=slurm_%A_%a.error
#SBATCH --output=slurm_%A_%a.out
#SBATCH --partition=general
#SBATCH --account=a_mcrae
#SBATCH --array=1-39

i=$SLURM_ARRAY_TASK_ID

TASKFILE="/QRISdata/Q5729/job_list.txt"
trait=$(sed -n "${i}p" $TASKFILE)
trait=$(echo "$trait" | sed 's/^[[:space:]]*//;s/[[:space:]]*$//')

echo "Trimmed Trait: '$trait'"
echo ${i}
trait_magma_dir="/scratch/project/genetic_data_analysis/uqali4/MAGMA_10kb_UKB20k_56778genes_pc"
metrics_dirs=("cepo_norm" "det.esw_s" "TDEP" "esmu" "ges.esw_s" "nsi.esw_s" "sclinker" "ep.esw_s")
for dir_name in "${metrics_dirs[@]}"; do
  cell_type="/QRISdata/Q5514/Binary_baseline1.1/CARE_pc/${dir_name}/MAGMA/top10.txt"
  mkdir -p /scratch/user/uqali4/geneset_res/PCgenes_background/CARE_pc/${dir_name}/MAGMA_100kb_based
  res_dir="/scratch/user/uqali4/geneset_res/PCgenes_background/CARE_pc/${dir_name}/MAGMA_100kb_based"
  /scratch/project/genetic_data_analysis/uqali4/software/magma --gene-results $trait_magma_dir/magma.${trait}.genes.raw --set-annot $cell_type --out $res_dir/${trait}
done
```





/QRISdata/Q5514/Binary_baseline1.1/HLCA_core_healthy_allgenes/LP/det.esw_s/MAGMA/top10.txt

# Bash Script to Submit Generated .sh Files
```{bash}
#!/bin/bash
cd /home/uqali4/uqali4/scripts/MGset/PC
# Define the file prefixes
file_prefixes=(
  "Kamath_2022_normal_pc"
  "Kamath_2022_normal"
  "CARE"
  "CARE_pc"
)

# Read the original script content
original_script="Kamath_2022_normal_pc_magma_geneset_benchmark_100kb.sh"
script_content=$(<"$original_script")

# Loop through each prefix and create a new script with the appropriate prefix
for prefix in "${file_prefixes[@]}"; do
  # Create a new file name based on the prefix
  new_script="${prefix}_magma_geneset_benchmark_100kb.sh"
  
  # Replace the original prefix with the new prefix in the content
  new_content="${script_content//Kamath_2022_normal_pc/$prefix}"
  
  # Write the modified content to the new file
  echo "$new_content" > "$new_script"
  
  echo "Generated script: $new_script"
done

```


cd /home/uqali4/scripts
vi HLCA_core_healthy_pc_magma_geneset_benchmark_100kb.sh
```{bash}
#!/bin/bash
#SBATCH --nodes=1
#SBATCH --ntasks-per-node=1
#SBATCH --cpus-per-task=18
#SBATCH --mem=10G
#SBATCH --time=48:00:00
#SBATCH --job-name=HLCA_core_healthy_pc_magma_geneset_benchmark_100kb
#SBATCH --error=/home/uqali4/jobs_sterr_stout/MAGMA_benchmark/slurm_%A_%a.error
#SBATCH --output=/home/uqali4/jobs_sterr_stout/MAGMA_benchmark/slurm_%A_%a.out
#SBATCH --partition=general
#SBATCH --account=a_mcrae
#SBATCH --array=1-39

i=$SLURM_ARRAY_TASK_ID

TASKFILE="/QRISdata/Q5729/job_list.txt"
trait=$(sed -n "${i}p" $TASKFILE)
trait=$(echo "$trait" | sed 's/^[[:space:]]*//;s/[[:space:]]*$//')

echo "Trimmed Trait: '$trait'"
echo ${i}
trait_magma_dir="/scratch/project/genetic_data_analysis/uqali4/MAGMA_10kb_UKB20k_56778genes_pc"
metrics_dirs=("cepo_norm" "det.esw_s" "TDEP" "esmu" "ges.esw_s" "nsi.esw_s" "sclinker" "ep.esw_s")
for dir_name in "${metrics_dirs[@]}"; do
  cell_type="/QRISdata/Q5514/Binary_baseline1.1/HLCA_core_healthy_pc/LP/${dir_name}/MAGMA/top10.txt"
  mkdir -p /scratch/user/uqali4/geneset_res/PCgenes_background/HLCA_core_healthy_pc/${dir_name}/MAGMA_100kb_based
  res_dir="/scratch/user/uqali4/geneset_res/PCgenes_background/HLCA_core_healthy_pc/${dir_name}/MAGMA_100kb_based"
  /scratch/project/genetic_data_analysis/uqali4/software/magma --gene-results $trait_magma_dir/magma.${trait}.genes.raw --set-annot $cell_type --out $res_dir/${trait}
done


```



cd /QRISdata/Q3999/tmp/Benchmark_association/geneset_res/PCgenes_background/ For all genes parts are wrong.

# Bash Script to Submit Generated .sh Files
```{bash}
#!/bin/bash
cd /home/uqali4/uqali4/scripts/MGset/PC
# Define the file prefixes
file_prefixes=(
  "HLCA_core_healthy_allgenes"
  "HLCA_core_healthy_pc"
)

# Read the original script content
original_script="HLCA_core_healthy_allgenes_LP_magma_geneset_benchmark_100kb.sh"
script_content=$(<"$original_script")

# Loop through each prefix and create a new script with the appropriate prefix
for prefix in "${file_prefixes[@]}"; do
  # Create a new file name based on the prefix
  new_script="${prefix}_magma_geneset_benchmark_100kb.sh"
  
  # Replace the original prefix with the new prefix in the content
  new_content="${script_content//HLCA_core_healthy_allgenes/$prefix}"
  
  # Write the modified content to the new file
  echo "$new_content" > "$new_script"
  
  echo "Generated script: $new_script"
done

```


# Submit all scripts:
```{bash}
sh_directory="/home/uqali4/uqali4/scripts/MGset/PC2"
# Loop through all *_MAGMA_scDRS.sh files in the directory
for sh_file in "$sh_directory"/*.sh; do
  
  # Submit the job using sbatch
  sbatch "$sh_file"
  
done
```


# Bash script that will submit all scripts in the /scratch/project/genetic_data_analysis/uqali4/scripts/MGset/PC directory, except tms_pc_magma_geneset_benchmark_100kb.sh and ts_pc_magma_geneset_benchmark_100kb.sh
```{bash}
#!/bin/bash
#!/bin/bash

# Define the directory containing the .sh files
script_dir="/scratch/project/genetic_data_analysis/uqali4/scripts/MGset/PC"

# Loop through all .sh files in the directory
for file in "$script_dir"/*.sh; do
    # Use sed to remove the specified string and overwrite the file
    sed -i 's|/home/uqali4/jobs_sterr_stout/MAGMA_benchmark/||g' "$file"
    
    # Print a message indicating the file has been processed
    echo "Processed: $file"
done


# Define the script directory
SCRIPT_DIR="/scratch/project/genetic_data_analysis/uqali4/scripts/MGset/PC"

# Exclude these two scripts
EXCLUDE1="tms_pc_magma_geneset_benchmark_100kb.sh"
EXCLUDE2="ts_pc_magma_geneset_benchmark_100kb.sh"

# Loop through each script in the directory
for script in "$SCRIPT_DIR"/*.sh; do
    # Get the base name of the script (without the directory path)
    base_script=$(basename "$script")

    # Check if the script is one of the excluded scripts
    if [[ "$base_script" != "$EXCLUDE1" && "$base_script" != "$EXCLUDE2" ]]; then
        # Submit the script using the appropriate command (e.g., sbatch for Slurm)
        echo "Submitting script: $base_script"
        sbatch "$script"
    else
        echo "Skipping excluded script: $base_script"
    fi
done

```


# Check all the subdirectories under and count how many gsa.out files are
```{bash}
#!/bin/bash

# Base directory


base_dir="/QRISdata/Q3999/tmp/Benchmark_association/geneset_res/PCgenes_background/ctd_2019_Smillie_normal_cellxgene"

base_dir="/QRISdata/Q3999/tmp/Benchmark_association/geneset_res/PCgenes_background/ctd_2019_Smillie_normal_cellxgene_pc"


base_dir="/QRISdata/Q3999/tmp/Benchmark_association/geneset_res/PCgenes_background/Kamath_2022_normal_pc"

# Loop through all subdirectories under MAGMA_100kb_based
for dir in "$base_dir"/*/MAGMA_100kb_based; do
    # Check if the directory exists
    if [ -d "$dir" ]; then
        echo "Checking directory: $dir"
        
        # Count the number of gsa.out files
        count=$(ls -l "$dir" | grep "gsa.out" | wc -l)
        
        echo "Number of gsa.out files in $dir: $count"
    else
        echo "Directory $dir does not exist."
    fi
done


base_dir="/QRISdata/Q3999/tmp/Benchmark_association/geneset_res/PCgenes_background/tms_pc"

# Loop through all subdirectories under MAGMA_100kb_based
for dir in "$base_dir"/*/MAGMA_100kb_based; do
    # Check if the directory exists
    if [ -d "$dir" ]; then
        echo "Checking directory: $dir"
        
        # Count the number of gsa.out files
        count=$(ls -l "$dir" | grep "gsa.out" | wc -l)
        
        echo "Number of gsa.out files in $dir: $count"
    else
        echo "Directory $dir does not exist."
    fi
done

base_dir="/scratch/user/uqali4/geneset_res/PCgenes_background/tms_pc"

# Loop through all subdirectories under MAGMA_100kb_based
for dir in "$base_dir"/*/MAGMA_100kb_based; do
    # Check if the directory exists
    if [ -d "$dir" ]; then
        echo "Checking directory: $dir"
        
        # Count the number of gsa.out files
        count=$(ls -l "$dir" | grep "gsa.out" | wc -l)
        
        echo "Number of gsa.out files in $dir: $count"
    else
        echo "Directory $dir does not exist."
    fi
done


base_dir="/scratch/user/uqali4/geneset_res/PCgenes_background/ctd_Fasolino_2022_Nat_Metab_normal_only_pc"

# Loop through all subdirectories under MAGMA_100kb_based
for dir in "$base_dir"/*/MAGMA_100kb_based; do
    # Check if the directory exists
    if [ -d "$dir" ]; then
        echo "Checking directory: $dir"
        
        # Count the number of gsa.out files
        count=$(ls -l "$dir" | grep "gsa.out" | wc -l)
        
        echo "Number of gsa.out files in $dir: $count"
    else
        echo "Directory $dir does not exist."
    fi
done



base_dir="/scratch/user/uqali4/geneset_res/PCgenes_background/ctd_FBM_Jardine_2021_Nature_pc"

# Loop through all subdirectories under MAGMA_100kb_based
for dir in "$base_dir"/*/MAGMA_100kb_based; do
    # Check if the directory exists
    if [ -d "$dir" ]; then
        echo "Checking directory: $dir"
        
        # Count the number of gsa.out files
        count=$(ls -l "$dir" | grep "gsa.out" | wc -l)
        
        echo "Number of gsa.out files in $dir: $count"
    else
        echo "Directory $dir does not exist."
    fi
done



base_dir="/scratch/user/uqali4/geneset_res/PCgenes_background/ctd_Cheng_2018_Cell_Reports_pc"

# Loop through all subdirectories under MAGMA_100kb_based
for dir in "$base_dir"/*/MAGMA_100kb_based; do
    # Check if the directory exists
    if [ -d "$dir" ]; then
        echo "Checking directory: $dir"
        
        # Count the number of gsa.out files
        count=$(ls -l "$dir" | grep "gsa.out" | wc -l)
        
        echo "Number of gsa.out files in $dir: $count"
    else
        echo "Directory $dir does not exist."
    fi
done


base_dir="/scratch/user/uqali4/geneset_res/PCgenes_background/HLCA_core_healthy_pc"

# Loop through all subdirectories under MAGMA_100kb_based
for dir in "$base_dir"/*/MAGMA_100kb_based; do
    # Check if the directory exists
    if [ -d "$dir" ]; then
        echo "Checking directory: $dir"
        
        # Count the number of gsa.out files
        count=$(ls -l "$dir" | grep "gsa.out" | wc -l)
        
        echo "Number of gsa.out files in $dir: $count"
    else
        echo "Directory $dir does not exist."
    fi
done
```

# Revise new version with checking if the results have been finished.
vi ts_pc_magma_geneset_benchmark_100kb.sh
```{bash}
#!/bin/bash
#SBATCH --nodes=1
#SBATCH --ntasks-per-node=1
#SBATCH --cpus-per-task=18
#SBATCH --mem=10G
#SBATCH --time=48:00:00
#SBATCH --job-name=ts_pc_magma_geneset_benchmark_100kb
#SBATCH --error=slurm_%A_%a.error
#SBATCH --output=slurm_%A_%a.out
#SBATCH --partition=general
#SBATCH --account=a_mcrae
#SBATCH --array=1-39

i=$SLURM_ARRAY_TASK_ID

TASKFILE="/QRISdata/Q5729/job_list.txt"
trait=$(sed -n "${i}p" $TASKFILE)
trait=$(echo "$trait" | sed 's/^[[:space:]]*//;s/[[:space:]]*$//')

echo "Trimmed Trait: '$trait'"
echo ${i}
trait_magma_dir="/scratch/project/genetic_data_analysis/uqali4/MAGMA_10kb_UKB20k_56778genes_pc_tms_ts_consist"
metrics_dirs=("cepo_norm" "det.esw_s" "TDEP" "esmu" "ges.esw_s" "nsi.esw_s" "sclinker" "ep.esw_s") #

for dir_name in "${metrics_dirs[@]}"; do
  cell_type="/QRISdata/Q5514/MGset_full/ts_pc/${dir_name}/MAGMA/top10.txt"
  mkdir -p /scratch/user/uqali4/geneset_res/PCgenes_background/ts_pc/${dir_name}/MAGMA_100kb_based
  res_dir="/scratch/user/uqali4/geneset_res/PCgenes_background/ts_pc/${dir_name}/MAGMA_100kb_based"
  
  # Check if the output file already exists
  output_file="${res_dir}/${trait}.gsa.out"
  if [ ! -f "$output_file" ]; then
    echo "Running MAGMA for $trait in $dir_name..."
    /scratch/project/genetic_data_analysis/uqali4/software/magma --gene-results $trait_magma_dir/magma.${trait}.genes.raw --set-annot $cell_type --out $res_dir/${trait}
  else
    echo "Output file $output_file already exists. Skipping..."
  fi
done

```

vi tms_pc_magma_geneset_benchmark_100kb.sh
```{bash}
#!/bin/bash
#SBATCH --nodes=1
#SBATCH --ntasks-per-node=1
#SBATCH --cpus-per-task=18
#SBATCH --mem=10G
#SBATCH --time=48:00:00
#SBATCH --job-name=tms_pc_magma_geneset_benchmark_100kb
#SBATCH --error=slurm_%A_%a.error
#SBATCH --output=slurm_%A_%a.out
#SBATCH --partition=general
#SBATCH --account=a_mcrae
#SBATCH --array=1-39

i=$SLURM_ARRAY_TASK_ID

TASKFILE="/QRISdata/Q5729/job_list.txt"
trait=$(sed -n "${i}p" $TASKFILE)
trait=$(echo "$trait" | sed 's/^[[:space:]]*//;s/[[:space:]]*$//')

echo "Trimmed Trait: '$trait'"
echo ${i}
trait_magma_dir="/scratch/project/genetic_data_analysis/uqali4/MAGMA_10kb_UKB20k_56778genes_pc_tms_ts_consist"
metrics_dirs=("cepo_norm" "det.esw_s" "TDEP" "esmu" "ges.esw_s" "nsi.esw_s" "sclinker" "ep.esw_s") #

for dir_name in "${metrics_dirs[@]}"; do
  cell_type="/QRISdata/Q5514/MGset_full/tms_pc/${dir_name}/MAGMA/top10.txt"
  mkdir -p /scratch/user/uqali4/geneset_res/PCgenes_background/tms_pc/${dir_name}/MAGMA_100kb_based
  res_dir="/scratch/user/uqali4/geneset_res/PCgenes_background/tms_pc/${dir_name}/MAGMA_100kb_based"
  
  # Check if the output file already exists
  output_file="${res_dir}/${trait}.gsa.out"
  if [ ! -f "$output_file" ]; then
    echo "Running MAGMA for $trait in $dir_name..."
    /scratch/project/genetic_data_analysis/uqali4/software/magma --gene-results $trait_magma_dir/magma.${trait}.genes.raw --set-annot $cell_type --out $res_dir/${trait}
  else
    echo "Output file $output_file already exists. Skipping..."
  fi
done

```


vi tms_pc_magma_geneset_benchmark_100kb.sh
```{bash}
#!/bin/bash
#SBATCH --nodes=1
#SBATCH --ntasks-per-node=1
#SBATCH --cpus-per-task=8
#SBATCH --mem=10G
#SBATCH --time=48:00:00
#SBATCH --job-name=tms_pc_magma_geneset_benchmark_100kb
#SBATCH --error=slurm_%A_%a.error
#SBATCH --output=slurm_%A_%a.out
#SBATCH --partition=general
#SBATCH --account=a_mcrae
#SBATCH --array=1-39

i=$SLURM_ARRAY_TASK_ID

TASKFILE="/QRISdata/Q5729/job_list.txt"
trait=$(sed -n "${i}p" $TASKFILE)
trait=$(echo "$trait" | sed 's/^[[:space:]]*//;s/[[:space:]]*$//')

echo "Trimmed Trait: '$trait'"
echo ${i}
trait_magma_dir="/scratch/project/genetic_data_analysis/uqali4/MAGMA_10kb_UKB20k_56778genes_pc_tms_ts_consist"
metrics_dirs=("esmu" "ges.esw_s" "nsi.esw_s" "sclinker" "ep.esw_s") #"cepo_norm" "det.esw_s" "TDEP" 

for dir_name in "${metrics_dirs[@]}"; do
  cell_type="/QRISdata/Q5514/MGset_full/tms_pc/${dir_name}/MAGMA/top10.txt"
  res_dir="/QRISdata/Q3999/tmp/Benchmark_association/geneset_res/PCgenes_background/tms_pc/${dir_name}/MAGMA_100kb_based"
  
  # Check if the output file already exists
  output_file="${res_dir}/${trait}.gsa.out"
  if [ ! -f "$output_file" ]; then
    echo "Running MAGMA for $trait in $dir_name..."
  mkdir -p /scratch/user/uqali4/geneset_res/PCgenes_background/tms_pc/${dir_name}/MAGMA_100kb_based
  new_res_dir="/scratch/user/uqali4/geneset_res/PCgenes_background/tms_pc/${dir_name}/MAGMA_100kb_based"
    /scratch/project/genetic_data_analysis/uqali4/software/magma --gene-results $trait_magma_dir/magma.${trait}.genes.raw --set-annot $cell_type --out $new_res_dir/${trait}
  else
    echo "Output file $output_file already exists. Skipping..."
  fi
done

```


vi ts_pc_magma_geneset_benchmark_100kb.sh
```{bash}
#!/bin/bash
#SBATCH --nodes=1
#SBATCH --ntasks-per-node=1
#SBATCH --cpus-per-task=8
#SBATCH --mem=10G
#SBATCH --time=48:00:00
#SBATCH --job-name=ts_pc_magma_geneset_benchmark_100kb
#SBATCH --error=slurm_%A_%a.error
#SBATCH --output=slurm_%A_%a.out
#SBATCH --partition=general
#SBATCH --account=a_mcrae
#SBATCH --array=1-39

i=$SLURM_ARRAY_TASK_ID

TASKFILE="/QRISdata/Q5729/job_list.txt"
trait=$(sed -n "${i}p" $TASKFILE)
trait=$(echo "$trait" | sed 's/^[[:space:]]*//;s/[[:space:]]*$//')

echo "Trimmed Trait: '$trait'"
echo ${i}
trait_magma_dir="/scratch/project/genetic_data_analysis/uqali4/MAGMA_10kb_UKB20k_56778genes_pc_tms_ts_consist"
metrics_dirs=("det.esw_s" "TDEP" "esmu" "ges.esw_s" "nsi.esw_s" "sclinker" "ep.esw_s") #"cepo_norm" 

for dir_name in "${metrics_dirs[@]}"; do
  cell_type="/QRISdata/Q5514/MGset_full/ts_pc/${dir_name}/MAGMA/top10.txt"
  res_dir="/QRISdata/Q3999/tmp/Benchmark_association/geneset_res/PCgenes_background/ts_pc/${dir_name}/MAGMA_100kb_based"
  
  # Check if the output file already exists
  output_file="${res_dir}/${trait}.gsa.out"
  if [ ! -f "$output_file" ]; then
    echo "Running MAGMA for $trait in $dir_name..."
  mkdir -p /scratch/user/uqali4/geneset_res/PCgenes_background/ts_pc/${dir_name}/MAGMA_100kb_based
  new_res_dir="/scratch/user/uqali4/geneset_res/PCgenes_background/ts_pc/${dir_name}/MAGMA_100kb_based"
    /scratch/project/genetic_data_analysis/uqali4/software/magma --gene-results $trait_magma_dir/magma.${trait}.genes.raw --set-annot $cell_type --out $new_res_dir/${trait}
  else
    echo "Output file $output_file already exists. Skipping..."
  fi
done

```

vi 2019_Smillie_normal_cellxgene_magma_geneset_benchmark_100kb.sh
```{bash}
#!/bin/bash
#SBATCH --nodes=1
#SBATCH --ntasks-per-node=1
#SBATCH --cpus-per-task=18
#SBATCH --mem=10G
#SBATCH --time=48:00:00
#SBATCH --job-name=2019_Smillie_normal_cellxgene_magma_geneset_benchmark_100kb
#SBATCH --error=slurm_%A_%a.error
#SBATCH --output=slurm_%A_%a.out
#SBATCH --partition=general
#SBATCH --account=a_mcrae
#SBATCH --array=1-39

i=$SLURM_ARRAY_TASK_ID

TASKFILE="/QRISdata/Q5729/job_list.txt"
trait=$(sed -n "${i}p" $TASKFILE)
trait=$(echo "$trait" | sed 's/^[[:space:]]*//;s/[[:space:]]*$//')

echo "Trimmed Trait: '$trait'"
echo ${i}
trait_magma_dir="/scratch/project/genetic_data_analysis/uqali4/MAGMA_10kb_UKB20k_56778genes_pc"
metrics_dirs=("esmu" "ges.esw_s" "nsi.esw_s" "sclinker") #"TDEP" "cepo_norm" "det.esw_s" "ep.esw_s" 
for dir_name in "${metrics_dirs[@]}"; do
  cell_type="/QRISdata/Q2120/biLDSC/${dir_name}/processed/ctd_2019_Smillie_normal_cellxgene/MAGMA/top10.txt"
  mkdir -p /QRISdata/Q3999/tmp/Benchmark_association/geneset_res/PCgenes_background/ctd_2019_Smillie_normal_cellxgene/${dir_name}/MAGMA_100kb_based
  res_dir="/QRISdata/Q3999/tmp/Benchmark_association/geneset_res/PCgenes_background/ctd_2019_Smillie_normal_cellxgene/${dir_name}/MAGMA_100kb_based"
  
  # Check if the output file already exists
  output_file="${res_dir}/${trait}.gsa.out"
  if [ ! -f "$output_file" ]; then
    echo "Running MAGMA for $trait in $dir_name..."
  mkdir -p /scratch/user/uqali4/geneset_res/PCgenes_background/ctd_2019_Smillie_normal_cellxgene/${dir_name}/MAGMA_100kb_based
  new_res_dir="/scratch/user/uqali4/geneset_res/PCgenes_background/ctd_2019_Smillie_normal_cellxgene/${dir_name}/MAGMA_100kb_based"
  /scratch/project/genetic_data_analysis/uqali4/software/magma --gene-results $trait_magma_dir/magma.${trait}.genes.raw --set-annot $cell_type --out $new_res_dir/${trait}
  else
    echo "Output file $output_file already exists. Skipping..."
  fi
done


```

cd /home/uqali4/scripts
vi 2019_Smillie_normal_cellxgene_pc_magma_geneset_benchmark_100kb.sh
```{bash}
#!/bin/bash
#SBATCH --nodes=1
#SBATCH --ntasks-per-node=1
#SBATCH --cpus-per-task=8
#SBATCH --mem=10G
#SBATCH --time=48:00:00
#SBATCH --job-name=ctd_2019_Smillie_normal_cellxgene_pc_magma_geneset_benchmark_100kb
#SBATCH --error=slurm_%A_%a.error
#SBATCH --output=slurm_%A_%a.out
#SBATCH --partition=general
#SBATCH --account=a_mcrae
#SBATCH --array=1-39

i=$SLURM_ARRAY_TASK_ID

TASKFILE="/QRISdata/Q5729/job_list.txt"
trait=$(sed -n "${i}p" $TASKFILE)
trait=$(echo "$trait" | sed 's/^[[:space:]]*//;s/[[:space:]]*$//')

echo "Trimmed Trait: '$trait'"
echo ${i}
trait_magma_dir="/scratch/project/genetic_data_analysis/uqali4/MAGMA_10kb_UKB20k_56778genes_pc"
metrics_dirs=("TDEP" "cepo_norm" "det.esw_s" "ep.esw_s" "esmu" "ges.esw_s" "nsi.esw_s" "sclinker") #"TDEP" "cepo_norm" "det.esw_s" "ep.esw_s" "esmu" 
for dir_name in "${metrics_dirs[@]}"; do
  cell_type="/QRISdata/Q2120/biLDSC/${dir_name}/processed/ctd_2019_Smillie_normal_cellxgene_pc/MAGMA/top10.txt"
  mkdir -p /scratch/user/uqali4/geneset_res/PCgenes_background/ctd_2019_Smillie_normal_cellxgene_pc/${dir_name}/MAGMA_100kb_based
  new_res_dir="/scratch/user/uqali4/geneset_res/PCgenes_background/ctd_2019_Smillie_normal_cellxgene_pc/${dir_name}/MAGMA_100kb_based"
  /scratch/project/genetic_data_analysis/uqali4/software/magma --gene-results $trait_magma_dir/magma.${trait}.genes.raw --set-annot $cell_type --out $new_res_dir/${trait}
done


```








